### 2018-06-29 paper/manuscript.tex
ENH: start a refnx paper

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{legalpaper, portrait, margin=1in}
\usepackage{mhchem}
\usepackage[affil-it]{authblk}

\begin{document}
\title{refnx - Neutron and X-ray reflectometry analysis in Python}
\author[1,*]{Andrew Nelson}
\author[2]{Stuart Prescott}

\affil[1]{% 
 Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232, Australia}
\affil[2]{School of Chemical Engineering, University of New South Wales,  Sydney, NSW, Australia}
\affil[*]{Corresponding author: Andrew.Nelson@ansto.gov.au}

\date{\today}

\newcommand{\refnx}{\emph{refnx }}
\newcommand{\Objective}{\textbf{Objective }}
\newcommand{\Parameter}{\textbf{Parameter }}
\newcommand{\Structure}{\textbf{Structure }}
\newcommand{\Slab}{\textbf{Slab }}
\newcommand{\Component}{\textbf{Component }}

\maketitle

\begin{abstract}
The \refnx package is designed for object oriented model based analysis of neutron and X-ray reflectometry data in Python. Structure construction is modular, being composed from a series of Components that each describe a subset of the interface. These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters. The Model and data are used to create an Objective, which is used calculate residuals, log-likelihood, and log-prior probabilities of the system. Objectives are combined to perform co-refinement of multiple datasets, and mixed area models. All parameters in the system can have a variety of Bounds applied; these bounds consist of probability distributions which represent their prior probability. The prior probability encodes a users knowledge about the Parameter values, which allows the curvefitting engine to direct solutions toward more probable parameter space. Extra prior probability terms can be defined for Components, over and above that available from the Parameters alone.
Algebraic Parameter constraints are available.
The powerful curvefitting engine offers the choice of using a normal least squares fitting approach (with a variety of global and gradient based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters. The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
The whole package is designed with a focus on reproducible research; its use in Jupyter notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to reproduce analyses made by others.
\end{abstract}

\subsection*{Introduction}
The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range [10, 5000]$\AA$ has exploded over the past years \cite{Wood2017, Daillant2009}. Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.  Several programs are available for this purpose, with a variety of different features \cite{Bjorck2007, Gerelli2016, Kienzle2011, Nelson2006}. These programs typically create a model of the interface, and incrementally refine the model against the data using least squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e. the statistical variation of the parameters in a model).

Given that there are more and more publications arising from the reflectometry technique, it is vital that the analysis is reproducible. Reproducibility in research is an underlying principle of science. Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses. One example for addressing this issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.

Here we outline a new reflectometry analysis package, \refnx (version number x.x is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking}.
These notebooks are a mix of executable code cells and markup. An analysis performed in such a notebook can be appended as supplementary information, along with the data, to an article. Readers can then replicate the exact data analysis, provided they have setup the same computing environment. Setting up the computing environment is simplified using the conda package manager \cite{conda}, and an environment file (although other approaches are available). To that end the Jupyter notebooks for the example analysis performed in this paper are appended as supplementary information.

\refnx has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions, model selection, etc.

The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior knowledge of the parameters and the likelihood (or the sum of the log-probabilities).

\begin{gather} 
\label{eqn:1}\ p(\theta | D, I) \propto p(\theta | I)\times p(D | \theta, I)\\
p(D | \theta, I) = -\frac{1}{2} \sum [(\frac{y_n - model} {\sigma_n})^2 + log(\sigma_n^2)]\label{eqn:2}
\end{gather}

The posterior distribution, $p(\theta | I, D)$, is the the probability of the parameters given the data, $D$, and prior knowledge about the system, $I$. 
The prior probability distribution, $p(\theta | I)$, is the state of knowledge that already exists about the parameters of interest, such as that obtained from other experiments.
The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $y_n$ (with uncertainties $\sigma_n$), given the model parameters and other prior information.  The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee}.

\subsection*{Method}
\refnx is written in Python with an object oriented design, Figure~\ref{fig:components}. As with \emph{Motofit} \cite{Nelson2006} it calculates reflectivity using the Abeles method \cite{Heavens1955} for specular reflection from a stratified medium.
The building block of the analysis is the \Parameter object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute. The bounds are a probability distribution - the simplest bound being a uniform distribution which would set a lower and upper limit for the parameter. This probability distribution is the prior probability for the parameter. Any of the \emph{scipy.stats} \cite{Jones2001-2017} continuous distributions, or distributions created by the user, can be used for this purpose. Algebraic relationships between \Parameter can be applied using constraints.
The \Structure object represents the interfacial model, comprising of individual \Component objects in series. Each \Component represents a subset of the interface and contains several physically relevant Parameters. The simplest \Component is a \Slab, which have a uniform scattering length density, thickness, roughness, and volume fraction of solvent. The simplest models are simply a series of \Slab. More sophisticated components include \textbf{LipidLeaflet} and \textbf{Spline}. \textbf{Spline} is designed for freeform modelling of an SLD profile using spline interpolation. In addition to its constituent parameters each \Component can also contribute to the log-prior probability. This is useful when a \Component has an derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system. Each \Component has a slabs property that represents the strata for its particular subset of the interface. A \Slab object has a single slice, a \textbf{LipidLeaflet} has two (head/tail regions), but the \textbf{Spline} Component has many. These slices have uniform scattering length density, and use the Nevot-Croce \cite{Nevot1980} to describe roughness between them. If a different roughness model is required then a 'microsliced' \Component could be written to accomodate that.
The \Structure object is used to construct a \textbf{ReflectModel} object. This object is responsible for calculating the resolution smeared reflectivity of the \Structure, scaling the data, and adding a linear background (via the scale and background Parameters). There are different types of smearing available - constant dQ/Q, point by point resolution smearing from the dataset of interest, or via a smearing kernel of arbitrary shape \cite{Nelson2014}.
The \Objective class uses the \textbf{ReflectModel} and a dataset \textbf{Data1D} to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model. The \Objective can be given a \textbf{Transform} object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q. Several \Objective can be combined to form a \textbf{GlobalObjective} for co-refinement. The object oriented nature allows \Parameter, \Component to be reused throughout the setup, thereby facilitating co-refinement. For an example please see \textbf{lipid.ipynb} in the supporting information.
The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system. \refnx uses the \emph{scipy} package for least squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters. Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation. Visualisation of the samples produced by MCMC sampling are done using the \emph{corner} package \cite{corner} for scatter plot matrices. On the conclusion of a fit/sampling run each \Parameter is updated and given a standard error. For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximates the standard deviation for a normally distributed statistic.

\begin{figure}
  \includegraphics[width=\linewidth]{components}
  \caption{Schematic showing the relationship between classes that make up a typical reflectometry curvefitting problem.}
  \label{fig:components}
\end{figure}

To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting GUI can be created in a Jupyter notebook, Figure~\ref{fig:gui}. This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.

\begin{figure}
  \includegraphics[width=\linewidth]{./datasets/gui.png}
  \caption{Screenshot of the Jupyter/ipywidgets GUI. Jupyter notebook available in supporting information.}
  \label{fig:gui}
\end{figure}

\subsection*{Example}
Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc. Multiple contrast variation measurements are necessary to reduce modelling ambiguity and improve the ability to determine the structure of various components in the system. The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule. Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an incoherent sum of reflectivities from different areas. \refnx has functionality for all these requirements, such as the LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and MixedReflectModel. It is straightforward to develop/modify new components for different structural functionality, a consequence of the object oriented approach. Here the \textbf{LipidLeafltet} is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \textbf{LipidLeaflet} does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane}. The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters. The area per molecule from the analysis, 57$\AA\pm1$, compares well to that measured by X-ray diffraction. Figure~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} shows the distribution of the posterior probability distribution around the data and in the SLD profile. These are obtained by random samples from the MCMC chain. The spread in SLD profiles is used to determine what range of structures is consistent with the data. Multi-modalities in these SLD profiles can be due to statistical uncertainties, the Q ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
%TODO use exact area per molecule, and use a reference for the Xray analysis

\begin{figure}%
\centering
\subfigure{%
\label{fig:global_fit}%
\includegraphics[width=5in]{./datasets/global_fit.png}}\hspace{1em}%
\subfigure{%
\label{fig:d2o_sld_spread}%
\includegraphics[width=5in]{./datasets/d2o_sld_spread.png}}\\%
\caption{a) Reflectivity from DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution. Dataset for \ce{Si} match offset by 0.1, \ce{H_2O} contrast offset by 0.001. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median. Jupyter notebook used for the analysis is attached in the supporting information.}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./datasets/corner}
  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.}
  \label{fig:corner}
\end{figure}

\subsection*{Distribution and Modification}
Each submodule in \refnx possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively. For example, there are tests that check that the reflectivity of a model is calculated correctly, or that the behaviour of a function is correct for the different possible inputs and code paths through it. Since the test suite is an integral part of the package each installation is testable.

 The source code for \refnx is held in a version controlled git repository hosted on github at https://www.github.com/refnx/refnx. Contributors create their own fork of the main \refnx repository, and create a feature branch to which they make modifications. They then submit a pull request (PR) against the main repository. The modifications made in the PR are checked on continuous integration (CI) web-services which runs the test suite against a matrix of Python versions on the macOS, Linux and Windows operating systems. If the tests pass, and the changes are considered useful, then the features are merged into the main repository. When a sufficient number of features have accumulated a new release is made. Successive releases have an incrementing semantic version number which can be obtained from the installed package, with each release being given its own DOI.

 The recommended way of using \refnx is from a conda environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx conda-forge channel. These distributables are made as part of the release process using the same CI web-services used to test the code. The matrix of distributables cover the major Python versions currently in use, across the macOS/Windows/Linux operating systems. Alternatively the package can be installed from source, either directly from the git repository, or via pip from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx). Building from source requires a C compiler and the \emph{Cython} and \emph{NumPy} packages to be installed. It's important to note that for reproducible research purposes both conda and pip can be used to install a specific version of \refnx.

\refnx is released under the BSD permissive open source licence. In addition its dependencies are released under open source licences which mean that use is free of cost to the end user.

\subsection*{Conclusions}\label{conclusions}
\refnx is a powerful tool for least squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with Jupyter notebooks. Its features include: MCMC sampling of posterior distribution for parameters (permitting model selection), structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a Jupyter/ipywidgets GUI

\subsection*{Acknowledgements}
We acknowledge x.x for the provision of the lipid bilayer datasets in the example.
%TODO insert name

\subsection*{Supporting information}
\textbf{gui.ipynb} - Jupyter notebook used to create the GUI screenshot.\\
\textbf{lipid.ipynb} - Jupyter notebook used for the lipid analysis example

\bibliography{main}{}
\bibliographystyle{unsrt}
\end{document}

### 2018-07-16 paper/manuscript.tex
PAPER: minor changes

@@
 \newcommand{\Component}{\textbf{Component }}
+\newcommand{\LipidLeaflet}{\textbf{LipidLeaflet }}
+\newcommand{\Spline}{\textbf{Spline }}
+\newcommand{\conda}{\emph{conda }}
+\newcommand{\MixedReflectModel}{\emph{MixedReflectModel }}
+\newcommand{\pip}{\emph{pip }}
+\newcommand{\NumPy}{\emph{NumPy }}
+\newcommand{\Cython}{\emph{Cython }}
+\newcommand{\Jupyter}{\emph{Jupyter }}
+\newcommand{\ipywidgets}{\emph{ipywidgets }}
 
@@
 \begin{abstract}
-The \refnx package is designed for object oriented model based analysis of neutron and X-ray reflectometry data in Python.
+The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python.
 Structure construction is modular, being composed from a series of Components that each describe a subset of the interface.
 These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters.
-The Model and data are used to create an Objective, which is used calculate residuals, log-likelihood, and log-prior probabilities of the system.
-Objectives are combined to perform co-refinement of multiple datasets, and mixed area models.
+The Model and data are used to create an Objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system.
+Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models.
 All parameters in the system can have a variety of Bounds applied; these bounds consist of probability distributions which represent their prior probability.
-The prior probability encodes a users knowledge about the Parameter values, which allows the curvefitting engine to direct solutions toward more probable parameter space.
-Extra prior probability terms can be defined for Components, over and above that available from the Parameters alone.
+The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space.
+Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone.
 Algebraic Parameter constraints are available.
-The powerful curvefitting engine offers the choice of using a normal least squares fitting approach (with a variety of global and gradient based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
+The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
 The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
-The whole package is designed with a focus on reproducible research; its use in Jupyter notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to reproduce analyses made by others.
+
+The whole package is designed with a focus on reproducible research; its use in \Jupyter notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to straightforwardly reproduce analyses made by others.
 \end{abstract}
@@
 Several programs are available for this purpose, with a variety of different features \cite{Bjorck2007, Gerelli2016, Kienzle2011, Nelson2006}.
-These programs typically create a model of the interface, and incrementally refine the model against the data using least squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e.
+These programs typically create a model of the interface, and incrementally refine the model against the data using least-squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e.
 the statistical variation of the parameters in a model).
@@
 Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
-One example for addressing this issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
+Even if the datasets and software packages used to analyse them are supplied in supplementary information (most often they are not), a comprehensive set of instructions would need to be provided.
+One example for addressing this reproducibility issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
 
-Here we outline a new reflectometry analysis package, \refnx (version number x.x is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking}.
+Here we outline a new reflectometry analysis package, \refnx (version number x.x is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
 These notebooks are a mix of executable code cells and markup.
 An analysis performed in such a notebook can be appended as supplementary information, along with the data, to an article.
-Readers can then replicate the exact data analysis, provided they have setup the same computing environment.
-Setting up the computing environment is simplified using the conda package manager \cite{conda}, and an environment file (although other approaches are available).
-To that end the Jupyter notebooks for the example analysis performed in this paper are appended as supplementary information.
+Readers can then replicate the exact data analysis, provided they have set up the same computing environment.
+Setting up the computing environment is simplified using the \conda package manager \cite{conda}, and an environment file (although other approaches are available).
+To that end the \Jupyter notebooks for the example analysis performed in this paper are appended as supplementary information.
 
@@
 
-The posterior distribution, $p(\theta | I, D)$, is the the probability of the parameters given the data, $D$, and prior knowledge about the system, $I$. 
+The posterior distribution, $p(\theta | I, D)$, is the probability of the parameters given the data, $D$, and prior knowledge about the system, $I$. 
 The prior probability distribution, $p(\theta | I)$, is the state of knowledge that already exists about the parameters of interest, such as that obtained from other experiments.
@@
 \subsection*{Method}
-\refnx is written in Python with an object oriented design, Figure~\ref{fig:components}.
+\refnx is written in Python with an object-oriented design, Figure~\ref{fig:components}.
 As with \emph{Motofit} \cite{Nelson2006} it calculates reflectivity using the Abeles method \cite{Heavens1955} for specular reflection from a stratified medium.
 The building block of the analysis is the \Parameter object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute.
-The bounds are a probability distribution - the simplest bound being a uniform distribution which would set a lower and upper limit for the parameter.
+The bounds are a probability distribution - the simplest bound being a uniform distribution which would set lower and upper limits for the parameter.
 This probability distribution is the prior probability for the parameter.
@@
 Each \Component represents a subset of the interface and contains several physically relevant Parameters.
-The simplest \Component is a \Slab, which have a uniform scattering length density, thickness, roughness, and volume fraction of solvent.
+The simplest \Component is a \Slab, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
 The simplest models are simply a series of \Slab.
-More sophisticated components include \textbf{LipidLeaflet} and \textbf{Spline}.
-\textbf{Spline} is designed for freeform modelling of an SLD profile using spline interpolation.
+More sophisticated components include \LipidLeaflet and \Spline.
+\Spline is designed for freeform modelling of an SLD profile using spline interpolation.
 In addition to its constituent parameters each \Component can also contribute to the log-prior probability.
-This is useful when a \Component has an derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system.
-Each \Component has a slabs property that represents the strata for its particular subset of the interface.
-A \Slab object has a single slice, a \textbf{LipidLeaflet} has two (head/tail regions), but the \textbf{Spline} Component has many.
-These slices have uniform scattering length density, and use the Nevot-Croce \cite{Nevot1980} to describe roughness between them.
+This is useful when a \Component has a derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system.
+Each \Component has a \emph{slabs} property that represents the strata for its particular subset of the interface.
+A \Slab object has a single slice because it is a single thickness of uniform SLD.
+A \LipidLeaflet can be made of two slices (head/tail regions), but the \Spline Component has many.
+These slices have uniform SLD, and use the Nevot-Croce \cite{Nevot1980} to describe roughness between them.
 If a different roughness model is required then a 'microsliced' \Component could be written to accomodate that.
@@
 Several \Objective can be combined to form a \textbf{GlobalObjective} for co-refinement.
-The object oriented nature allows \Parameter, \Component to be reused throughout the setup, thereby facilitating co-refinement.
+The object-oriented nature allows \Parameter, \Component to be reused throughout the setup, thereby facilitating co-refinement.
 For an example please see \textbf{lipid.ipynb} in the supporting information.
 The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx uses the \emph{scipy} package for least squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.
-Visualisation of the samples produced by MCMC sampling are done using the \emph{corner} package \cite{corner} for scatter plot matrices.
+Visualisation of the samples produced by MCMC sampling is done using the \emph{corner} package \cite{corner} for scatter plot matrices.
 On the conclusion of a fit/sampling run each \Parameter is updated and given a standard error.
@@
   \includegraphics[width=\linewidth]{components}
-  \caption{Schematic showing the relationship between classes that make up a typical reflectometry curvefitting problem.}
+  \caption{Schematic showing the relationship between classes that make up a typical reflectometry curve-fitting problem.}
   \label{fig:components}
@@
 
-To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting GUI can be created in a Jupyter notebook, Figure~\ref{fig:gui}.
+To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting GUI can be created in a \Jupyter notebook, Figure~\ref{fig:gui}.
 This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.
@@
   \includegraphics[width=\linewidth]{./datasets/gui.png}
-  \caption{Screenshot of the Jupyter/ipywidgets GUI. Jupyter notebook available in supporting information.}
+  \caption{Screenshot of the \Jupyter/\ipywidgets GUI. \Jupyter notebook available in supporting information.}
   \label{fig:gui}
@@
 Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc.
-Multiple contrast variation measurements are necessary to reduce modelling ambiguity and improve the ability to determine the structure of various components in the system.
+Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information) and improve the ability to determine the structure of various components in the system.
 The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule.
-Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an incoherent sum of reflectivities from different areas.
-\refnx has functionality for all these requirements, such as the LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and MixedReflectModel.
-It is straightforward to develop/modify new components for different structural functionality, a consequence of the object oriented approach.
-Here the \textbf{LipidLeafltet} is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \textbf{LipidLeaflet} does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane}.
-The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters.
-The area per molecule from the analysis, 57$\AA\pm1$, compares well to that measured by X-ray diffraction.
-Figure~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} shows the distribution of the posterior probability distribution around the data and in the SLD profile.
+Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas.
+\refnx has functionality for all these requirements, such as the \LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel.
+It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach.
+Here the \LipidLeaflet is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
+The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$.
+Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
 These are obtained by random samples from the MCMC chain.
@@
 \includegraphics[width=5in]{./datasets/d2o_sld_spread.png}}\\%
-\caption{a) Reflectivity from DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution.
+\caption{a) Reflectivity from a DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution.
 Dataset for \ce{Si} match offset by 0.1, \ce{H_2O} contrast offset by 0.001.
 b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median.
-Jupyter notebook used for the analysis is attached in the supporting information.}
+\Jupyter notebook used for the analysis is attached in the supporting information.}
 \end{figure}
@@
 They then submit a pull request (PR) against the main repository.
-The modifications made in the PR are checked on continuous integration (CI) web-services which runs the test suite against a matrix of Python versions on the macOS, Linux and Windows operating systems.
+The modifications made in the PR are checked on continuous integration (CI) web-services which run the test suite against a matrix of Python versions on the macOS, Linux and Windows operating systems.
 If the tests pass, and the changes are considered useful, then the features are merged into the main repository.
@@
 
- The recommended way of using \refnx is from a conda environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx conda-forge channel.
+ The recommended way of using \refnx is from a \conda environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx conda-forge channel.
 These distributables are made as part of the release process using the same CI web-services used to test the code.
@@
 Alternatively the package can be installed from source, either directly from the git repository, or via pip from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
-Building from source requires a C compiler and the \emph{Cython} and \emph{NumPy} packages to be installed.
-It's important to note that for reproducible research purposes both conda and pip can be used to install a specific version of \refnx.
+Building from source requires a C compiler and the \Cython and \NumPy packages to be installed.
+It's important to note that for reproducible research purposes both \conda and \pip can be used to install a specific version of \refnx.
 
@@
 \subsection*{Conclusions}\label{conclusions}
-\refnx is a powerful tool for least squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with Jupyter notebooks.
-Its features include: MCMC sampling of posterior distribution for parameters (permitting model selection), structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a Jupyter/ipywidgets GUI
+\refnx is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter notebooks.
+Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a \Jupyter/\ipywidgets GUI
 
 \subsection*{Acknowledgements}
-We acknowledge x.x for the provision of the lipid bilayer datasets in the example.
+We acknowledge Anton Le Brun for the provision of the lipid bilayer datasets in the example.
 %TODO insert name
@@
 \subsection*{Supporting information}
-\textbf{gui.ipynb} - Jupyter notebook used to create the GUI screenshot.\\
-\textbf{lipid.ipynb} - Jupyter notebook used for the lipid analysis example
+\textbf{gui.ipynb} - \Jupyter notebook used to create the GUI screenshot.\\
+\textbf{lipid.ipynb} - \Jupyter notebook used for the lipid analysis example
 

### 2018-07-16 paper/manuscript.tex
PAPER

@@
 
-The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior knowledge of the parameters and the likelihood (or the sum of the log-probabilities).
+The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities).
 
@@
 Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc.
-Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information) and improve the ability to determine the structure of various components in the system.
+Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information in the scattering experiment) and improve the ability to determine the structure of various components in the system.
 The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule.

### 2018-07-17 paper/manuscript.tex
PAPER: address couple of comments

@@
 \begin{abstract}
-The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python.
+The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
 Structure construction is modular, being composed from a series of Components that each describe a subset of the interface.
@@
 \refnx uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
+However, other types of measurement errors (e.g.
+Poissonian) could be implemented by a subclass of \Objective and overriding the log-likelihood method.
 Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.

### 2018-07-17 paper/manuscript.tex
PAPER: address comments

@@
 \newcommand{\LipidLeaflet}{\textbf{LipidLeaflet }}
+\newcommand{\DataD}{\textbf{Data1D }}
+\newcommand{\ReflectModel}{\textbf{ReflectModel }}
 \newcommand{\Spline}{\textbf{Spline }}
@@
 The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
+
 Structure construction is modular, being composed from a series of Components that each describe a subset of the interface.
@@
 Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models.
-All parameters in the system can have a variety of Bounds applied; these bounds consist of probability distributions which represent their prior probability.
+All parameters in the system can have a variety of Bounds applied; these Bounds consist of probability distributions which represent their prior probability.
 The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space.
@@
 Algebraic Parameter constraints are available.
+
 The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
@@
 Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
-Even if the datasets and software packages used to analyse them are supplied in supplementary information (most often they are not), a comprehensive set of instructions would need to be provided.
+Even if the datasets and software packages used to analyse them are supplied in supplementary information (most often they are not), a comprehensive, ordered, set of instructions would need to be provided.
 One example for addressing this reproducibility issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
 
-Here we outline a new reflectometry analysis package, \refnx (version number x.x is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
+Here we outline a new reflectometry analysis package, \refnx (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
 These notebooks are a mix of executable code cells and markup.
@@
 Algebraic relationships between \Parameter can be applied using constraints.
+
 The \Structure object represents the interfacial model, comprising of individual \Component objects in series.
@@
 A \LipidLeaflet can be made of two slices (head/tail regions), but the \Spline Component has many.
-These slices have uniform SLD, and use the Nevot-Croce \cite{Nevot1980} to describe roughness between them.
+These slices have uniform SLD, and use the Nevot-Croce approach \cite{Nevot1980} to describe roughness between them.
 If a different roughness model is required then a 'microsliced' \Component could be written to accomodate that.
-The \Structure object is used to construct a \textbf{ReflectModel} object.
+
+The \Structure object is used to construct a \ReflectModel object.
 This object is responsible for calculating the resolution smeared reflectivity of the \Structure, scaling the data, and adding a linear background (via the scale and background Parameters).
-There are different types of smearing available - constant dQ/Q, point by point resolution smearing from the dataset of interest, or via a smearing kernel of arbitrary shape \cite{Nelson2014}.
-The \Objective class uses the \textbf{ReflectModel} and a dataset \textbf{Data1D} to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
+There are different types of smearing available - constant dQ/Q, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
+The constant $dQ/Q$ and point-by-point smearing use Gaussian convolution, with $dQ$ representing the FWHM of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
+
+The \Objective class uses the \ReflectModel and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
+The \DataD object has \emph{x, y, y\_err, x\_err} attributes to represent Q, R, dR, dQ.
+The \DataD object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
+A three column dataset represents Q ($\AA^{-1}$), R, dR (1 standard deviation).
+A four column dataset represents Q, R, dR, dQ ($\AA^{-1}$).
+Subclassing \DataD would allow other formats to be read.
+One example of this could be an wavelength dispersive file using $\Omega, \lambda$ data instead of Q; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers in order to account for absorption terms.
+In such a case \ReflectModel could be subclassed to make full use of this information.
 The \Objective can be given a \textbf{Transform} object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
@@
 For an example please see \textbf{lipid.ipynb} in the supporting information.
+
 The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
@@
 However, other types of measurement errors (e.g.
-Poissonian) could be implemented by a subclass of \Objective and overriding the log-likelihood method.
+Poissonian) could be implemented by a subclass of \Objective  overriding the log-likelihood method.
 Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.
@@
 This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.
+A fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
 

### 2018-07-17 paper/manuscript.tex
PAPER: answering comments

@@
 \newcommand{\NumPy}{\emph{NumPy }}
+\newcommand{\SciPy}{\emph{SciPy }}
 \newcommand{\Cython}{\emph{Cython }}
@@
 
-\subsection*{Introduction}
+\section*{Introduction}
 The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range [10, 5000]$\AA$ has exploded over the past years \cite{Wood2017, Daillant2009}.
@@
 
-\subsection*{Method}
+\section*{Method}
 \refnx is written in Python with an object-oriented design, Figure~\ref{fig:components}.
@@
 The \Objective class uses the \ReflectModel and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
-The \DataD object has \emph{x, y, y\_err, x\_err} attributes to represent Q, R, dR, dQ.
+The \DataD object has \emph{x, y, y\_err, x\_err} attributes to represent $Q, R, dR, dQ$.
 The \DataD object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
@@
 The object-oriented nature allows \Parameter, \Component to be reused throughout the setup, thereby facilitating co-refinement.
-For an example please see \textbf{lipid.ipynb} in the supporting information.
 
@@
 A fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
+For a comprehensive demonstration of multiple contrast co-refinement see \textbf{lipid.ipynb}, \textbf{lipid.pdf} in the supporting information.
 
@@
 
-\subsection*{Distribution and Modification}
+\section*{Distribution and Modification}
 Each submodule in \refnx possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively.
@@
 The matrix of distributables cover the major Python versions currently in use, across the macOS/Windows/Linux operating systems.
-Alternatively the package can be installed from source, either directly from the git repository, or via pip from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
+Alternatively the package can be installed from source, either directly from the git repository, or via \pip from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
 Building from source requires a C compiler and the \Cython and \NumPy packages to be installed.
-It's important to note that for reproducible research purposes both \conda and \pip can be used to install a specific version of \refnx.
 
@@
 
-\subsection*{Conclusions}\label{conclusions}
+\section*{Comments on reproducibility of analyses}
+In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
+\begin{itemize}
+  \item the datasets used need to be deposited with a journal article, or be freely available.
+  \item the exact software environment needs to be recreateable.
+  \item the exact ordered set of steps taken during the analysis needs to be listed.
+\end{itemize} 
+Each of these points are frequently neglected.
+For example, the use of different software versions may change the output from an analysis.
+The use of a GUI program may not record the full set of steps, or options, applied by a user.
+Whilst it is unable to meet the first criteria by itself the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken.
+The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc).
+At a later date those exact versions can be installed in the same Python version using one of: the \conda package manager, by installing from the source at a given version tag in the git repository, or by \pip.
+\conda can use environment files to recreate a specific setup.
+An alternative way of recreating the environment is a virtual machine, such as Docker.
+The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
+This has important implications for verifiability.
+%TODO finish verifiability...
+Open source - the user can look at the code for correctness, with unit testing we can see if things are calculated correctly.
+With closed source we have no idea if there are major problems with certain parts of an algorithm.
+%\refnx relies on a fully open software stack, with full traceability of every single line of code.
+
+\section*{Conclusions}\label{conclusions}
 \refnx is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter notebooks.
@@
 
-\subsection*{Acknowledgements}
-We acknowledge Anton Le Brun for the provision of the lipid bilayer datasets in the example.
-%TODO insert name
+\section*{Acknowledgements}
+We acknowledge Anton Le Brun for the provision of the lipid bilayer datasets in the example, and James Hester for comments made on the draft manuscript.
 
@@
 \textbf{gui.ipynb} - \Jupyter notebook used to create the GUI screenshot.\\
-\textbf{lipid.ipynb} - \Jupyter notebook used for the lipid analysis example
+\textbf{lipid.ipynb} - \Jupyter notebook used for the lipid analysis example.\\
+\textbf{lipid.pdf} - PDF view of the \Jupyter notebook used for the lipid analysis example.\\
+\textbf{refnx-paper.yml} - \conda environment file to reproduce the analysis environment in this paper.
 

### 2018-07-17 paper/manuscript.tex
PAPER: small change

@@
 Each of these points are frequently neglected.
-For example, the use of different software versions may change the output from an analysis.
-The use of a GUI program may not record the full set of steps, or options, applied by a user.
+For example, the use of different software versions may change the output from an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
 Whilst it is unable to meet the first criteria by itself the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken.
@@
 An alternative way of recreating the environment is a virtual machine, such as Docker.
-The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
+The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult/impossible with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
 This has important implications for verifiability.

### 2018-07-17 paper/manuscript.tex
PAPER: verifiability

@@
 An alternative way of recreating the environment is a virtual machine, such as Docker.
-The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult/impossible with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
-This has important implications for verifiability.
-%TODO finish verifiability...
-Open source - the user can look at the code for correctness, with unit testing we can see if things are calculated correctly.
-With closed source we have no idea if there are major problems with certain parts of an algorithm.
-%\refnx relies on a fully open software stack, with full traceability of every single line of code.
+The ordered set of steps to perform the analysis is recordable in the \Jupyter notebook.
+The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here - the ability to return to a specific software version/environment is often difficult with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
+Moreover, there are important ramifications for verifiability.
+\refnx is based on a fully open software stack, with good unit test coverage.
+The user can run tests for each component and inspect parts for correctness.
+For example, the behaviour of the reflectivity calculation in \refnx is checked from first principles in the test suite; and can be done now and in several years time.
+If problems are discovered, they can be corrected.
+With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors.
+Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.
 
@@
 \section*{Acknowledgements}
-We acknowledge Anton Le Brun for the provision of the lipid bilayer datasets in the example, and James Hester for comments made on the draft manuscript.
+We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Isaac Gresham (UNSW) for important feedback on refnx development.
 

### 2018-07-17 paper/manuscript.tex
PAPER: minor manuscript changes

@@
 Each of these points are frequently neglected.
-For example, the use of different software versions may change the output from an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
-Whilst it is unable to meet the first criteria by itself the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken.
+For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
+Whilst it is unable to meet the first criteria by itself, the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken.
 The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc).
@@
 If problems are discovered, they can be corrected.
-With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors.
+With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors; one has to rely on trust.
 Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.

### 2018-07-17 paper/manuscript.tex
PAPER: reproducibility comments

@@
 
-To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting GUI can be created in a \Jupyter notebook, Figure~\ref{fig:gui}.
+To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting graphical user interface (GUI) can be created in a \Jupyter notebook, Figure~\ref{fig:gui}.
 This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.
@@
   \item the datasets used need to be deposited with a journal article, or be freely available.
-  \item the exact software environment needs to be recreateable.
+  \item the exact software environment needs to be recreatable.
   \item the exact ordered set of steps taken during the analysis needs to be listed.
 \end{itemize} 
-Each of these points are frequently neglected.
+Each of these points are often omitted in the literature.
 For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
@@
 \conda can use environment files to recreate a specific setup.
-An alternative way of recreating the environment is a virtual machine, such as Docker.
+An alternative way of recreating the environment is by using a virtual machine, such as Docker.
 The ordered set of steps to perform the analysis is recordable in the \Jupyter notebook.
-The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here - the ability to return to a specific software version/environment is often difficult with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis.
+The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here.
+With closed source or proprietary software the ability to return to a specific software version/environment can be difficult, different versions can have modifications that can change the output of an analysis.
+In addition accessibility (due to cost, etc) to the wider scientific community can also hinder reproducibility.
 Moreover, there are important ramifications for verifiability.

### 2018-07-17 paper/manuscript.tex
PAPER: backslashes

@@
 
-\newcommand{\refnx}{\emph{refnx }}
-\newcommand{\Objective}{\textbf{Objective }}
-\newcommand{\Parameter}{\textbf{Parameter }}
-\newcommand{\Structure}{\textbf{Structure }}
-\newcommand{\Slab}{\textbf{Slab }}
-\newcommand{\Component}{\textbf{Component }}
-\newcommand{\LipidLeaflet}{\textbf{LipidLeaflet }}
-\newcommand{\DataD}{\textbf{Data1D }}
-\newcommand{\ReflectModel}{\textbf{ReflectModel }}
-\newcommand{\Spline}{\textbf{Spline }}
-\newcommand{\conda}{\emph{conda }}
-\newcommand{\MixedReflectModel}{\emph{MixedReflectModel }}
-\newcommand{\pip}{\emph{pip }}
-\newcommand{\NumPy}{\emph{NumPy }}
-\newcommand{\SciPy}{\emph{SciPy }}
-\newcommand{\Cython}{\emph{Cython }}
-\newcommand{\Jupyter}{\emph{Jupyter }}
-\newcommand{\ipywidgets}{\emph{ipywidgets }}
+\newcommand{\refnx}{\emph{refnx}}
+\newcommand{\Objective}{\textbf{Objective}}
+\newcommand{\Parameter}{\textbf{Parameter}}
+\newcommand{\Structure}{\textbf{Structure}}
+\newcommand{\Slab}{\textbf{Slab}}
+\newcommand{\Component}{\textbf{Component}}
+\newcommand{\LipidLeaflet}{\textbf{LipidLeaflet}}
+\newcommand{\DataD}{\textbf{Data1D}}
+\newcommand{\ReflectModel}{\textbf{ReflectModel}}
+\newcommand{\Spline}{\textbf{Spline}}
+\newcommand{\conda}{\emph{conda}}
+\newcommand{\MixedReflectModel}{\emph{MixedReflectModel}}
+\newcommand{\pip}{\emph{pip}}
+\newcommand{\NumPy}{\emph{NumPy}}
+\newcommand{\SciPy}{\emph{SciPy}}
+\newcommand{\Cython}{\emph{Cython}}
+\newcommand{\Jupyter}{\emph{Jupyter}}
+\newcommand{\ipywidgets}{\emph{ipywidgets}}
 
@@
 \begin{abstract}
-The \refnx package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
+The \refnx\ package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
 
@@
 
-The whole package is designed with a focus on reproducible research; its use in \Jupyter notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to straightforwardly reproduce analyses made by others.
+The whole package is designed with a focus on reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to straightforwardly reproduce analyses made by others.
 \end{abstract}
@@
 
-Here we outline a new reflectometry analysis package, \refnx (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
+Here we outline a new reflectometry analysis package, \refnx\ (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
 These notebooks are a mix of executable code cells and markup.
@@
 Readers can then replicate the exact data analysis, provided they have set up the same computing environment.
-Setting up the computing environment is simplified using the \conda package manager \cite{conda}, and an environment file (although other approaches are available).
-To that end the \Jupyter notebooks for the example analysis performed in this paper are appended as supplementary information.
+Setting up the computing environment is simplified using the \conda\ package manager \cite{conda}, and an environment file (although other approaches are available).
+To that end the \Jupyter\ notebooks for the example analysis performed in this paper are appended as supplementary information.
 
-\refnx has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions, model selection, etc.
+\refnx\ has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions, model selection, etc.
 
@@
 \section*{Method}
-\refnx is written in Python with an object-oriented design, Figure~\ref{fig:components}.
+\refnx\ is written in Python with an object-oriented design, Figure~\ref{fig:components}.
 As with \emph{Motofit} \cite{Nelson2006} it calculates reflectivity using the Abeles method \cite{Heavens1955} for specular reflection from a stratified medium.
-The building block of the analysis is the \Parameter object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute.
+The building block of the analysis is the \Parameter\ object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute.
 The bounds are a probability distribution - the simplest bound being a uniform distribution which would set lower and upper limits for the parameter.
@@
 Any of the \emph{scipy.stats} \cite{Jones2001-2017} continuous distributions, or distributions created by the user, can be used for this purpose.
-Algebraic relationships between \Parameter can be applied using constraints.
+Algebraic relationships between \Parameter\ can be applied using constraints.
 
-The \Structure object represents the interfacial model, comprising of individual \Component objects in series.
-Each \Component represents a subset of the interface and contains several physically relevant Parameters.
-The simplest \Component is a \Slab, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
-The simplest models are simply a series of \Slab.
-More sophisticated components include \LipidLeaflet and \Spline.
-\Spline is designed for freeform modelling of an SLD profile using spline interpolation.
-In addition to its constituent parameters each \Component can also contribute to the log-prior probability.
-This is useful when a \Component has a derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system.
-Each \Component has a \emph{slabs} property that represents the strata for its particular subset of the interface.
-A \Slab object has a single slice because it is a single thickness of uniform SLD.
-A \LipidLeaflet can be made of two slices (head/tail regions), but the \Spline Component has many.
+The \Structure\ object represents the interfacial model, comprising of individual \Component\ objects in series.
+Each \Component\ represents a subset of the interface and contains several physically relevant Parameters.
+The simplest \Component\ is a \Slab\, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
+The simplest models are simply a series of \Slab\.
+More sophisticated components include \LipidLeaflet\ and \Spline\.
+\Spline\ is designed for freeform modelling of an SLD profile using spline interpolation.
+In addition to its constituent parameters each \Component\ can also contribute to the log-prior probability.
+This is useful when a \Component\ has a derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system.
+Each \Component\ has a \emph{slabs} property that represents the strata for its particular subset of the interface.
+A \Slab\ object has a single slice because it is a single thickness of uniform SLD.
+A \LipidLeaflet\ can be made of two slices (head/tail regions), but the \Spline\ Component has many.
 These slices have uniform SLD, and use the Nevot-Croce approach \cite{Nevot1980} to describe roughness between them.
-If a different roughness model is required then a 'microsliced' \Component could be written to accomodate that.
+If a different roughness model is required then a 'microsliced' \Component\ could be written to accomodate that.
 
-The \Structure object is used to construct a \ReflectModel object.
-This object is responsible for calculating the resolution smeared reflectivity of the \Structure, scaling the data, and adding a linear background (via the scale and background Parameters).
+The \Structure\ object is used to construct a \ReflectModel\ object.
+This object is responsible for calculating the resolution smeared reflectivity of the \Structure\, scaling the data, and adding a linear background (via the scale and background Parameters).
 There are different types of smearing available - constant dQ/Q, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
-The constant $dQ/Q$ and point-by-point smearing use Gaussian convolution, with $dQ$ representing the FWHM of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
+The constant $dQ/Q$ and point-by-point smearing use Gaussian convolution, with $dQ$ representing the full width half maximum (FWHM) of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
 
-The \Objective class uses the \ReflectModel and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
+The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
 The \DataD object has \emph{x, y, y\_err, x\_err} attributes to represent $Q, R, dR, dQ$.
@@
 Subclassing \DataD would allow other formats to be read.
-One example of this could be an wavelength dispersive file using $\Omega, \lambda$ data instead of Q; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers in order to account for absorption terms.
-In such a case \ReflectModel could be subclassed to make full use of this information.
-The \Objective can be given a \textbf{Transform} object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
-Several \Objective can be combined to form a \textbf{GlobalObjective} for co-refinement.
-The object-oriented nature allows \Parameter, \Component to be reused throughout the setup, thereby facilitating co-refinement.
+One example of this could be an wavelength dispersive file using $\Omega, \lambda$ data instead of Q; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
+In such a case \ReflectModel\ could be subclassed to make full use of this information.
+The \Objective\ can be given a \textbf{Transform} object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
+Several \Objective\ can be combined to form a \textbf{GlobalObjective} for co-refinement.
+The object-oriented nature allows \Parameter\, \Component\ to be reused throughout the setup, thereby facilitating co-refinement.
 
-The \Objective statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
+\refnx\ uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
 However, other types of measurement errors (e.g.
-Poissonian) could be implemented by a subclass of \Objective  overriding the log-likelihood method.
+Poissonian) could be implemented by a subclass of \Objective\  overriding the log-likelihood method.
 Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.
 Visualisation of the samples produced by MCMC sampling is done using the \emph{corner} package \cite{corner} for scatter plot matrices.
-On the conclusion of a fit/sampling run each \Parameter is updated and given a standard error.
+On the conclusion of a fit/sampling run each \Parameter\ is updated and given a standard error.
 For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximates the standard deviation for a normally distributed statistic.
@@
 
-To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting graphical user interface (GUI) can be created in a \Jupyter notebook, Figure~\ref{fig:gui}.
+To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting graphical user interface (GUI) can be created in a \Jupyter\ notebook, Figure~\ref{fig:gui}.
 This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{./datasets/gui.png}
-  \caption{Screenshot of the \Jupyter/\ipywidgets GUI. \Jupyter notebook available in supporting information.}
+  \includegraphics[width=\linewidth]{./supporting_information/gui.png}
+  \caption{Screenshot of the \Jupyter\/\ipywidgets\ GUI. \Jupyter\ notebook available in supporting information.}
   \label{fig:gui}
@@
 Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas.
-\refnx has functionality for all these requirements, such as the \LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel.
+\refnx\ has functionality for all these requirements, such as the \LipidLeaflet\ component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel\.
 It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach.
-Here the \LipidLeaflet is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
+Here the \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
 The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$.
@@
 \label{fig:global_fit}%
-\includegraphics[width=5in]{./datasets/global_fit.png}}\hspace{1em}%
+\includegraphics[width=5in]{./supporting_information/global_fit.png}}\hspace{1em}%
 \subfigure{%
 \label{fig:d2o_sld_spread}%
-\includegraphics[width=5in]{./datasets/d2o_sld_spread.png}}\\%
+\includegraphics[width=5in]{./supporting_information/d2o_sld_spread.png}}\\%
 \caption{a) Reflectivity from a DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution.
@@
 b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median.
-\Jupyter notebook used for the analysis is attached in the supporting information.}
+\Jupyter\ notebook used for the analysis is attached in the supporting information.}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{./datasets/corner}
+  \includegraphics[width=\linewidth]{./supporting_information/corner}
   \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.}
@@
 \section*{Distribution and Modification}
-Each submodule in \refnx possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively.
+Each submodule in \refnx\ possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively.
 For example, there are tests that check that the reflectivity of a model is calculated correctly, or that the behaviour of a function is correct for the different possible inputs and code paths through it.
@@
 
- The source code for \refnx is held in a version controlled git repository hosted on github at https://www.github.com/refnx/refnx.
-Contributors create their own fork of the main \refnx repository, and create a feature branch to which they make modifications.
+ The source code for \refnx\ is held in a version controlled git repository hosted on github at https://www.github.com/refnx/refnx.
+Contributors create their own fork of the main \refnx\ repository, and create a feature branch to which they make modifications.
 They then submit a pull request (PR) against the main repository.
@@
 
- The recommended way of using \refnx is from a \conda environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx conda-forge channel.
+ The recommended way of using \refnx\ is from a \conda\ environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx\ conda-forge channel.
 These distributables are made as part of the release process using the same CI web-services used to test the code.
 The matrix of distributables cover the major Python versions currently in use, across the macOS/Windows/Linux operating systems.
-Alternatively the package can be installed from source, either directly from the git repository, or via \pip from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
-Building from source requires a C compiler and the \Cython and \NumPy packages to be installed.
+Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
+Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.
 
-\refnx is released under the BSD permissive open source licence. In addition its dependencies are released under open source licences which mean that use is free of cost to the end user.
+\refnx\ is released under the BSD permissive open source licence. In addition its dependencies are released under open source licences which mean that use is free of cost to the end user.
 
@@
 For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
-Whilst it is unable to meet the first criteria by itself, the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken.
-The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc).
-At a later date those exact versions can be installed in the same Python version using one of: the \conda package manager, by installing from the source at a given version tag in the git repository, or by \pip.
-\conda can use environment files to recreate a specific setup.
+Whilst it is unable to meet the first criteria by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken.
+The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx\, \SciPy\, \NumPy\, Python, etc).
+At a later date those exact versions can be installed in the same Python version using one of: the \conda\ package manager, by installing from the source at a given version tag in the git repository, or by \pip\.
+\conda\ can use environment files to recreate a specific setup.
 An alternative way of recreating the environment is by using a virtual machine, such as Docker.
-The ordered set of steps to perform the analysis is recordable in the \Jupyter notebook.
+The ordered set of steps to perform the analysis is recordable in the \Jupyter\ notebook.
 The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here.
@@
 Moreover, there are important ramifications for verifiability.
-\refnx is based on a fully open software stack, with good unit test coverage.
+\refnx\ is based on a fully open software stack, with good unit test coverage.
 The user can run tests for each component and inspect parts for correctness.
-For example, the behaviour of the reflectivity calculation in \refnx is checked from first principles in the test suite; and can be done now and in several years time.
+For example, the behaviour of the reflectivity calculation in \refnx\ is checked from first principles in the test suite; and can be done now and in several years time.
 If problems are discovered, they can be corrected.
@@
 \section*{Conclusions}\label{conclusions}
-\refnx is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter notebooks.
-Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a \Jupyter/\ipywidgets GUI
+\refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks.
+Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a \Jupyter\/\ipywidgets\ GUI
 
@@
 \subsection*{Supporting information}
-\textbf{gui.ipynb} - \Jupyter notebook used to create the GUI screenshot.\\
-\textbf{lipid.ipynb} - \Jupyter notebook used for the lipid analysis example.\\
-\textbf{lipid.pdf} - PDF view of the \Jupyter notebook used for the lipid analysis example.\\
-\textbf{refnx-paper.yml} - \conda environment file to reproduce the analysis environment in this paper.
+\textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
+\textbf{lipid.ipynb} - \Jupyter\ notebook used for the lipid analysis example.\\
+\textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
+\textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.
 

### 2018-07-19 paper/manuscript.tex
PAPER: manuscript changes

@@
 \newcommand{\Objective}{\textbf{Objective}}
+\newcommand{\GlobalObjective}{\textbf{GlobalObjective}}
 \newcommand{\Parameter}{\textbf{Parameter}}
@@
 \newcommand{\LipidLeaflet}{\textbf{LipidLeaflet}}
+\newcommand{\Transform}{\textbf{Transform}}
 \newcommand{\DataD}{\textbf{Data1D}}
@@
 \newcommand{\conda}{\emph{conda}}
+\newcommand{\corner}{\emph{corner}}
 \newcommand{\MixedReflectModel}{\emph{MixedReflectModel}}
 \newcommand{\pip}{\emph{pip}}
+\newcommand{\emcee}{\emph{emcee}}
 \newcommand{\NumPy}{\emph{NumPy}}
@@
 
-\refnx\ has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions, model selection, etc.
+\refnx\ has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions for the parameters, model selection, etc.
 
@@
 \label{eqn:1}\ p(\theta | D, I) \propto p(\theta | I)\times p(D | \theta, I)\\
-p(D | \theta, I) = -\frac{1}{2} \sum [(\frac{y_n - model} {\sigma_n})^2 + log(\sigma_n^2)]\label{eqn:2}
+p(D | \theta, I) = -\frac{1}{2} \sum \left[\left(\frac{y_n - model} {\sigma_n}\right)^2 + log(\sigma_n^2)\right]\label{eqn:2}
 \end{gather}
 
-The posterior distribution, $p(\theta | I, D)$, is the probability of the parameters given the data, $D$, and prior knowledge about the system, $I$. 
-The prior probability distribution, $p(\theta | I)$, is the state of knowledge that already exists about the parameters of interest, such as that obtained from other experiments.
-The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $y_n$ (with uncertainties $\sigma_n$), given the model parameters and other prior information.
+The prior distribution, $p(\theta | I)$, is the probability of a parameter, $\theta$, given preexisting knowledge of the system, $I$.
+For example, a prior could be a simple Uniform distribution that specifies a lower and upper bound, or a normal distribution that represents an experimentally derived value.
+The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information.
+It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $model$.
+
+The posterior distribution, $p(\theta | I, D)$, is the probability of the parameters given the data and prior knowledge about the system.
 The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee}.
+At the end of an MCMC run the parameter set possesses a number of samples (called a 'chain'), whose statistics reveal the distribution and covariance of the parameters, the spread of the model around the data, and in a reflectometry context the range of structures that are consistent with the data.
 
@@
 The building block of the analysis is the \Parameter\ object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute.
-The bounds are a probability distribution - the simplest bound being a uniform distribution which would set lower and upper limits for the parameter.
-This probability distribution is the prior probability for the parameter.
+The bounds are a probability distribution representing the prior.
 Any of the \emph{scipy.stats} \cite{Jones2001-2017} continuous distributions, or distributions created by the user, can be used for this purpose.
@@
 The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
-The \DataD object has \emph{x, y, y\_err, x\_err} attributes to represent $Q, R, dR, dQ$.
-The \DataD object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
+The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q, R, dR, dQ$.
+The \DataD\ object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
 A three column dataset represents Q ($\AA^{-1}$), R, dR (1 standard deviation).
 A four column dataset represents Q, R, dR, dQ ($\AA^{-1}$).
-Subclassing \DataD would allow other formats to be read.
+Subclassing \DataD\ would allow other formats to be read.
 One example of this could be an wavelength dispersive file using $\Omega, \lambda$ data instead of Q; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
-In such a case \ReflectModel\ could be subclassed to make full use of this information.
-The \Objective\ can be given a \textbf{Transform} object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
-Several \Objective\ can be combined to form a \textbf{GlobalObjective} for co-refinement.
-The object-oriented nature allows \Parameter\, \Component\ to be reused throughout the setup, thereby facilitating co-refinement.
+In such a case \ReflectModel\ could be subclassed to make full use of this energy dispersive information.
+An \Objective\ can be given a \Transform\ object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
+Several \Objective\ can be combined to form a \GlobalObjective\ for co-refinement.
+The object-oriented nature allows \Parameter\, \Component\ to be reused in in different \Objective, thereby facilitating co-refinement.
 
 The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \emph{scipy} package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emph{emcee} package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emcee\ package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
@@
 Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.
-Visualisation of the samples produced by MCMC sampling is done using the \emph{corner} package \cite{corner} for scatter plot matrices.
-On the conclusion of a fit/sampling run each \Parameter\ is updated and given a standard error.
-For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximates the standard deviation for a normally distributed statistic.
+Visualisation of the samples produced by MCMC sampling is done using the \corner\ package \cite{corner} for scatter plot matrices.
+On the conclusion of a fit/sampling run each \Parameter\ value is updated and given a standard error.
+For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.
 
@@
 A fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
-For a comprehensive demonstration of multiple contrast co-refinement see \textbf{lipid.ipynb}, \textbf{lipid.pdf} in the supporting information.
+For a comprehensive demonstration of multiple contrast co-refinement see the annotated notebook in the supporting information.
 
@@
 Here the \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
+The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supplementary information.
 The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$.
@@
 Dataset for \ce{Si} match offset by 0.1, \ce{H_2O} contrast offset by 0.001.
-b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median.
-\Jupyter\ notebook used for the analysis is attached in the supporting information.}
+b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median.}
 \end{figure}
@@
 \section*{Conclusions}\label{conclusions}
-\refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks.
-Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, interparameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a \Jupyter\/\ipywidgets\ GUI
+\refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and with extensibility in mind.
+Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, algebraic inter-parameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a (\Jupyter\) \ipywidgets\ GUI.
 
 \section*{Acknowledgements}
-We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Isaac Gresham (UNSW) for important feedback on refnx development.
+We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on refnx development.
 

### 2018-07-19 paper/manuscript.tex
PAPER: minor mods

@@
 The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supplementary information.
-The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$.
+The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57.0$\AA\pm0.15$.
 Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
@@
 \refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and with extensibility in mind.
-Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, algebraic inter-parameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a (\Jupyter\) \ipywidgets\ GUI.
+Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, algebraic inter-parameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a (\Jupyter\ ) \ipywidgets\ GUI.
 

### 2018-07-19 paper/manuscript.tex
PAPER: mention benchmarking
PAPER: reminder to describe how lipid leaflet works

@@
 It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach.
-Here the \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
+%describe lipidLeaflet TODO The \LipidLeaflet\ component
+Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
 The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supplementary information.
@@
 Since the test suite is an integral part of the package each installation is testable.
+In addition, there is a benchmarking suite to track changes in performance, specifically the speed of critical calculations, over time.
 

### 2018-07-19 paper/manuscript.tex
PAPER: flesh out lipid example section

@@
 \newcommand{\corner}{\emph{corner}}
-\newcommand{\MixedReflectModel}{\emph{MixedReflectModel}}
+\newcommand{\MixedReflectModel}{\textbf{MixedReflectModel}}
 \newcommand{\pip}{\emph{pip}}
@@
 
-The whole package is designed with a focus on reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supplementary information, permits scientists to straightforwardly reproduce analyses made by others.
+The whole package is designed with a focus on reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits scientists to straightforwardly reproduce analyses made by others.
 \end{abstract}
@@
 Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
-Even if the datasets and software packages used to analyse them are supplied in supplementary information (most often they are not), a comprehensive, ordered, set of instructions would need to be provided.
+Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions would need to be provided.
 One example for addressing this reproducibility issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
@@
 These notebooks are a mix of executable code cells and markup.
-An analysis performed in such a notebook can be appended as supplementary information, along with the data, to an article.
+An analysis performed in such a notebook can be appended as supporting information, along with the data, to an article.
 Readers can then replicate the exact data analysis, provided they have set up the same computing environment.
 Setting up the computing environment is simplified using the \conda\ package manager \cite{conda}, and an environment file (although other approaches are available).
-To that end the \Jupyter\ notebooks for the example analysis performed in this paper are appended as supplementary information.
+To that end the \Jupyter\ notebooks for the example analysis performed in this paper are appended as supporting information.
 
@@
 The simplest \Component\ is a \Slab\, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
-The simplest models are simply a series of \Slab\.
-More sophisticated components include \LipidLeaflet\ and \Spline\.
+The simplest models are simply a series of \Slab.
+More sophisticated components include \LipidLeaflet\ and \Spline.
 \Spline\ is designed for freeform modelling of an SLD profile using spline interpolation.
@@
 Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas.
-\refnx\ has functionality for all these requirements, such as the \LipidLeaflet\ component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel\.
+\refnx\ has functionality for all these requirements, such as the \LipidLeaflet\ component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel.
 It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach.
-%describe lipidLeaflet TODO The \LipidLeaflet\ component
+
+The parameters used in the \LipidLeaflet\ component are: area per molecule ($A$), thicknesses for each of the head and tail regions ($t_x$), sums of scattering lengths of the head and tail regions ($b_x$), partial volumes of the head and tail groups ($V_x$), roughness between head and tail region, and SLDs of the solvents for the head and tail group ($\rho_{x, solv}$).
+The overall SLD of each of the head and tail group regions are given by Equations~\ref{eqn:3} and \ref{eqn:4}.
+The approach used in this component ensures that there is a 1:1 correspondence of heads to tails.
+%TODO cite a paper which gives a whole load of volumes?
+\begin{gather} 
+\label{eqn:3} \phi_{x} = \frac{V_x}{At_x}\\
+\rho_x =  \phi_{x} \frac{b_x}{V_x} + (1 - \phi_{x})\rho_{x, solv} \label{eqn:4}
+\end{gather}
+
+By default the head and tail solvents are assumed to be the same as the solvent that is used throughout the \Structure.
+This will be the case when using \LipidLeaflet\ for a solid-liquid reflectometry experiment.
+However, at the air-liquid, or liquid-liquid interfaces the solvent for the head and tail region may be different, and it is possible to use different solvent SLDs for each.
+We note that the \LipidLeaflet\ component may also be used to describe other amphiphiles adsorbing at an interface.
+
 Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
-The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supplementary information.
-The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57.0$\AA\pm0.15$.
+Two \LipidLeaflet\ are required to describe the inner and outer leaflets of a bilayer, the component contains an attribute which can reverse the direction of one of the leaflets.
+The use of individual objects to describe each leaflet leads to great flexibility; it becomes easy to model asymmetric bilayers (inner leaflet can be a different lipid to the outer lipid), and one can model interstitial water layers between the leaflets as well.
+
+The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supporting information.
+The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of $57.0 \pm0.15 \AA$.
 Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
@@
 Multi-modalities in these SLD profiles can be due to statistical uncertainties, the Q ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
-%TODO use exact area per molecule, and use a reference for the Xray analysis
+%TODO A reference for V_m?
 
@@
 The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx\, \SciPy\, \NumPy\, Python, etc).
-At a later date those exact versions can be installed in the same Python version using one of: the \conda\ package manager, by installing from the source at a given version tag in the git repository, or by \pip\.
+At a later date those exact versions can be installed in the same Python version using one of: the \conda\ package manager, by installing from the source at a given version tag in the git repository, or by \pip.
 \conda\ can use environment files to recreate a specific setup.
@@
 \section*{Acknowledgements}
-We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on refnx development.
+We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on \refnx\ development.
 

### 2018-07-21 paper/manuscript.tex
PAPER: generalised curvefitting
PAPER: how long it takes

@@
 The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
+Whilst the main intention of the program is to analyse reflectometry data it is equally adept for generalised curve-fitting purposes.
 
@@
 The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden–Fletcher–Goldfarb–Shanno with bounds) and the  \emcee\ package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden-€“Fletcher-€“Goldfarb-€“Shanno with bounds) and the  \emcee\ package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
@@
   \includegraphics[width=\linewidth]{./supporting_information/corner}
-  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.}
+  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.
+The sampling took $\sim$12 minutes for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
   \label{fig:corner}

### 2018-07-21 paper/manuscript.tex
PAPER: formatting

@@
 Whilst it is unable to meet the first criteria by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken.
-The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx\, \SciPy\, \NumPy\, Python, etc).
+The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc).
 At a later date those exact versions can be installed in the same Python version using one of: the \conda\ package manager, by installing from the source at a given version tag in the git repository, or by \pip.

### 2018-07-22 paper/manuscript.tex
PAPER:ptemcee

@@
 \newcommand{\emcee}{\emph{emcee}}
+\newcommand{\ptemcee}{\emph{ptemcee}}
 \newcommand{\NumPy}{\emph{NumPy}}
@@
 
-The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities).
+The posterior probability distribution for a parameter set in Bayesian statistics, Equation~\ref{eqn:1}, is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities).
 
@@
 The posterior distribution, $p(\theta | I, D)$, is the probability of the parameters given the data and prior knowledge about the system.
-The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee}.
+The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee, ptemcee}.
 At the end of an MCMC run the parameter set possesses a number of samples (called a 'chain'), whose statistics reveal the distribution and covariance of the parameters, the spread of the model around the data, and in a reflectometry context the range of structures that are consistent with the data.
@@
 The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden-€“Fletcher-€“Goldfarb-€“Shanno with bounds) and the  \emcee\ package \cite{emcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden-€“Fletcher-€“Goldfarb-€“Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
 The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
@@
   \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.
-The sampling took $\sim$12 minutes for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
+The sampling took $\sim$13 minutes on a 3.2GHz quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
   \label{fig:corner}

### 2018-07-23 paper/manuscript.tex
Specify mhchem version
Fix maths and units

@@
 \usepackage{geometry}
+\usepackage[separate-uncertainty=true]{siunitx}
 \geometry{legalpaper, portrait, margin=1in}
-\usepackage{mhchem}
+\usepackage[version=4]{mhchem}
 \usepackage[affil-it]{authblk}
@@
 \section*{Introduction}
-The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range [10, 5000]$\AA$ has exploded over the past years \cite{Wood2017, Daillant2009}.
+The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has exploded over the past years \cite{Wood2017, Daillant2009}.
 Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.
@@
 This object is responsible for calculating the resolution smeared reflectivity of the \Structure\, scaling the data, and adding a linear background (via the scale and background Parameters).
-There are different types of smearing available - constant dQ/Q, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
-The constant $dQ/Q$ and point-by-point smearing use Gaussian convolution, with $dQ$ representing the full width half maximum (FWHM) of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
+There are different types of smearing available - constant $\mathrm{d}Q/Q$, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
+The constant $\mathrm{d}Q/Q$ and point-by-point smearing use Gaussian convolution, with $\mathrm{d}Q$ representing the full width half maximum (FWHM) of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
 
 The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
-The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q, R, dR, dQ$.
+The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$.
 The \DataD\ object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
-A three column dataset represents Q ($\AA^{-1}$), R, dR (1 standard deviation).
-A four column dataset represents Q, R, dR, dQ ($\AA^{-1}$).
+A three column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$ (1 standard deviation).
+A four column dataset represents $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}).
 Subclassing \DataD\ would allow other formats to be read.
-One example of this could be an wavelength dispersive file using $\Omega, \lambda$ data instead of Q; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
+One example of this could be an wavelength dispersive file using $\Omega$, $\lambda$ data instead of $Q$; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
 In such a case \ReflectModel\ could be subclassed to make full use of this energy dispersive information.
-An \Objective\ can be given a \Transform\ object to permit fitting as log-R vs Q, $RQ^4$ vs Q, or lin-R vs Q.
+An \Objective\ can be given a \Transform\ object to permit fitting as $\log R$ vs $Q$, $RQ^4$ vs $Q$, or $R$ vs $Q$.
 Several \Objective\ can be combined to form a \GlobalObjective\ for co-refinement.
 The object-oriented nature allows \Parameter\, \Component\ to be reused in in different \Objective, thereby facilitating co-refinement.
+%FIXME: above said 'lin-R' is that linear or natural log (\ln)
 
 The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden-€“Fletcher-€“Goldfarb-€“Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 \ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
@@
 
-Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
+Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=\SI{2.07E-6}{\per\square\angstrom}], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
 Two \LipidLeaflet\ are required to describe the inner and outer leaflets of a bilayer, the component contains an attribute which can reverse the direction of one of the leaflets.
@@
 The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supporting information.
-The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of $57.0 \pm0.15 \AA$.
+The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of \SI{57.0 \pm0.15}{\square\angstrom}.
 Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
@@
 %TODO A reference for V_m?
+%FIXME units of area per molecule were wrong; check
 

### 2018-07-23 paper/manuscript.tex

@@
-\documentclass[12pt]{article}
-\usepackage{graphicx}
-\usepackage{subfigure}
+\documentclass[pdf,preprint]{iucr}
+\RequirePackage{graphicx}
+\journalcode{A}
+
+% \usepackage{subfigure}
 \usepackage{amsmath}
-\usepackage{geometry}
 \usepackage[separate-uncertainty=true]{siunitx}
-\geometry{legalpaper, portrait, margin=1in}
 \usepackage[version=4]{mhchem}
-\usepackage[affil-it]{authblk}
 
@@
 \title{refnx - Neutron and X-ray reflectometry analysis in Python}
-\author[1,*]{Andrew Nelson}
-\author[2]{Stuart Prescott}
+\cauthor[a]{Andrew}{Nelson}{andrew.nelson@ansto.gov.au}{}
+\author[b]{Stuart~W.}{Prescott}
 
-\affil[1]{% 
- Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232, Australia}
-\affil[2]{School of Chemical Engineering, University of New South Wales,  Sydney, NSW, Australia}
-\affil[*]{Corresponding author: Andrew.Nelson@ansto.gov.au}
+\aff[a]{Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232 \country{Australia}}
+\aff[b]{School of Chemical Engineering, University of New South Wales,  Sydney, NSW, 2052 \country{Australia}}
 
@@
 
+\begin{synopsis}
+%TODO synopsis for ToC
+\end{synopsis}
+
 \begin{abstract}
@@
 
-\section*{Introduction}
+\section{Introduction}
 The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has exploded over the past years \cite{Wood2017, Daillant2009}.
@@
 
-\section*{Method}
+\section{Method}
 \refnx\ is written in Python with an object-oriented design, Figure~\ref{fig:components}.
@@
 The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
+\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
 \ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{components}
+  \includegraphics[width=175mm]{components}
   \caption{Schematic showing the relationship between classes that make up a typical reflectometry curve-fitting problem.}
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{./supporting_information/gui.png}
-  \caption{Screenshot of the \Jupyter\/\ipywidgets\ GUI. \Jupyter\ notebook available in supporting information.}
+  \includegraphics[width=85mm]{./supporting_information/gui.png}
+  \caption{Screenshot of the \Jupyter/\ipywidgets\ GUI. \Jupyter\ notebook available in supporting information.}
   \label{fig:gui}
@@
 
-\subsection*{Example}
+\subsection{Example}
 Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc.
@@
 \centering
-\subfigure{%
 \label{fig:global_fit}%
-\includegraphics[width=5in]{./supporting_information/global_fit.png}}\hspace{1em}%
-\subfigure{%
+\includegraphics[width=85mm]{./supporting_information/global_fit.png}%
 \label{fig:d2o_sld_spread}%
-\includegraphics[width=5in]{./supporting_information/d2o_sld_spread.png}}\\%
+\includegraphics[width=85mm]{./supporting_information/d2o_sld_spread.png}
 \caption{a) Reflectivity from a DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution.
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{./supporting_information/corner}
+  \includegraphics[width=175mm]{./supporting_information/corner.png}
   \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.
@@
 
-\section*{Distribution and Modification}
+\section{Distribution and Modification}
 Each submodule in \refnx\ possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively.
@@
 
-\section*{Comments on reproducibility of analyses}
+\section{Comments on reproducibility of analyses}
 In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
@@
 
-\section*{Conclusions}\label{conclusions}
+\section{Conclusions}\label{conclusions}
 \refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and with extensibility in mind.
@@
 
-\section*{Acknowledgements}
+\section{Acknowledgements}
 We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on \refnx\ development.
 
-\subsection*{Supporting information}
+\subsection{Supporting information}
 \textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
@@
 \bibliography{main}{}
-\bibliographystyle{unsrt}
+\bibliographystyle{iucr}
 \end{document}

### 2018-07-23 paper/manuscript.tex
PAPER: journal code
PAPER: middle initials

@@
 \RequirePackage{graphicx}
-\journalcode{A}
+\journalcode{J}
 
@@
 \title{refnx - Neutron and X-ray reflectometry analysis in Python}
-\cauthor[a]{Andrew}{Nelson}{andrew.nelson@ansto.gov.au}{}
+\cauthor[a]{Andrew~R. J.}{Nelson}{andrew.nelson@ansto.gov.au}{}
 \author[b]{Stuart~W.}{Prescott}
@@
 \newcommand{\Objective}{\textbf{Objective}}
+\newcommand{\CurveFitter}{\textbf{CurveFitter}}
 \newcommand{\GlobalObjective}{\textbf{GlobalObjective}}
@@
 
-The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system.
+The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting or Bayesian MCMC of the system.
 \refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.

### 2018-07-24 paper/manuscript.tex
Use en dash in title
Further latex/cls fixes

@@
 \begin{document}
-\title{refnx - Neutron and X-ray reflectometry analysis in Python}
+\title{refnx -- Neutron and X-ray reflectometry analysis in Python}
 \cauthor[a]{Andrew~R. J.}{Nelson}{andrew.nelson@ansto.gov.au}{}
@@
 \section{Introduction}
+
 The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has exploded over the past years \cite{Wood2017, Daillant2009}.
@@
 Several programs are available for this purpose, with a variety of different features \cite{Bjorck2007, Gerelli2016, Kienzle2011, Nelson2006}.
-These programs typically create a model of the interface, and incrementally refine the model against the data using least-squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e.
-the statistical variation of the parameters in a model).
+These programs typically create a model of the interface, and incrementally refine the model against the data using least-squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).
 
@@
 
-Here we outline a new reflectometry analysis package, \refnx\ (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa} using a Python kernel \footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}.
+Here we outline a new reflectometry analysis package, \refnx\ (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa} using a Python kernel.\footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}
 These notebooks are a mix of executable code cells and markup.
@@
 The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee, ptemcee}.
-At the end of an MCMC run the parameter set possesses a number of samples (called a 'chain'), whose statistics reveal the distribution and covariance of the parameters, the spread of the model around the data, and in a reflectometry context the range of structures that are consistent with the data.
+At the end of an MCMC run the parameter set possesses a number of samples (called a `chain'), whose statistics reveal the distribution and covariance of the parameters, the spread of the model around the data, and in a reflectometry context the range of structures that are consistent with the data.
 
 \section{Method}
+
 \refnx\ is written in Python with an object-oriented design, Figure~\ref{fig:components}.
@@
 These slices have uniform SLD, and use the Nevot-Croce approach \cite{Nevot1980} to describe roughness between them.
-If a different roughness model is required then a 'microsliced' \Component\ could be written to accomodate that.
+If a different roughness model is required then a `microsliced' \Component\ could be written to accomodate that.
 
@@
 To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting graphical user interface (GUI) can be created in a \Jupyter\ notebook, Figure~\ref{fig:gui}.
-This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the 'To code' code generation button.
+This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the `To code' code generation button.
 A fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
@@
 \subsection{Example}
+
 Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc.
@@
 
-Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=\SI{2.07E-6}{\per\square\angstrom}], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}.
-Two \LipidLeaflet\ are required to describe the inner and outer leaflets of a bilayer, the component contains an attribute which can reverse the direction of one of the leaflets.
+Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=\SI{2.07E-6}{\per\square\angstrom}], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phospho\-choline (DMPC) bilayer at the solid-liquid interface, Figure~\ref{fig:global_fit}.\footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.} Two \LipidLeaflet\ are required to describe the inner and outer leaflets of a bilayer, the component contains an attribute which can reverse the direction of one of the leaflets.
 The use of individual objects to describe each leaflet leads to great flexibility; it becomes easy to model asymmetric bilayers (inner leaflet can be a different lipid to the outer lipid), and one can model interstitial water layers between the leaflets as well.
@@
 The \Jupyter\ notebook used for the analysis, \emph{lipid.ipynb}, is available in the supporting information.
-The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of \SI{57.0 \pm0.15}{\square\angstrom}.
+The corner plot (Figure~\ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of \SI{57.0 \pm0.15}{\square\angstrom}.
 Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
@@
   \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.
-The sampling took $\sim$13 minutes on a 3.2GHz quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
+The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
   \label{fig:corner}
@@
 \section{Distribution and Modification}
+
 Each submodule in \refnx\ possesses its own unit testing code for checking that the functions and classes in the module operate correctly, both individually and collectively.
@@
 \section{Comments on reproducibility of analyses}
+
 In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
@@
 \section{Conclusions}\label{conclusions}
+
 \refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and with extensibility in mind.
@@
 
-\section{Acknowledgements}
-We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on \refnx\ development.
+\ack{Acknowledgements:
+We acknowledge Anton Le Brun (ANSTO) for the provision of the lipid bilayer datasets in the example, James Hester (ANSTO) for comments made on the draft manuscript, and Andrew McCluskey (Bath University) and Isaac Gresham (UNSW) for important feedback on \refnx\ development.}
 
-\subsection{Supporting information}
+\section{Supporting information}
+
+\noindent
 \textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\

### 2018-07-24 paper/manuscript.tex
Add ref to reproducible workflow paper

@@
 Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
-Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions would need to be provided.
+Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions or a codified workflow would need to be provided \cite{Moeller2017a}.
 One example for addressing this reproducibility issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.

### 2018-07-24 paper/manuscript.tex
Include conda ref at distribution text

@@
 
- The recommended way of using \refnx\ is from a \conda\ environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx\ conda-forge channel.
+The recommended way of using \refnx\ is from a \conda\ environment, which offers package, dependency and environment management \cite{conda}, using the pre-compiled distributables on the \refnx\ conda-forge channel.
 These distributables are made as part of the release process using the same CI web-services used to test the code.
-The matrix of distributables cover the major Python versions currently in use, across the macOS/Windows/Linux operating systems.
-Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx).
-Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.
+The matrix of distributables cover the major Python versions currently in use, across the macOS, Windows, and Linux operating systems.
+Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI.
+\footnote{https://pypi.python.org/pypi/refnx} Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.
 

### 2018-07-24 paper/manuscript.tex
Make abstract single paragraph as required
Trim down abstract to manageable length

@@
 The \refnx\ package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
-
-Structure construction is modular, being composed from a series of Components that each describe a subset of the interface.
-These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters.
-The Model and data are used to create an Objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system.
+Model construction is modular, being composed from a series of components that each describe a subset of the interface, parameterised in terms of physically relevant parameters (volume fraction of a polymer, lipid area per molecule, etc).
+The model and data are used to create an objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system.
 Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models.
-All parameters in the system can have a variety of Bounds applied; these Bounds consist of probability distributions which represent their prior probability.
-The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space.
+Prior knowledge of parameter values is encoded as probability distribution functions or bounds on all parameters in the system.
 Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone.
 Algebraic Parameter constraints are available.
-
-The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
+A choice of fitting approaches is available include least-squares (global and gradient-based optimizers) and a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
 The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
-Whilst the main intention of the program is to analyse reflectometry data it is equally adept for generalised curve-fitting purposes.
-
-The whole package is designed with a focus on reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits scientists to straightforwardly reproduce analyses made by others.
+The package is designed to facilitate reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits straightforward reproduction of analyses.
 \end{abstract}

### 2018-07-31 paper/manuscript.tex
Specify UTF-8 for the source encoding
It is 2018, after all.
PAPER: cite Millman

@@
 
-% \usepackage{subfigure}
+\usepackage[utf8]{inputenc}
+
 \usepackage{amsmath}
-\usepackage[separate-uncertainty=true]{siunitx}
+\usepackage{siunitx}
+\sisetup{
+  separate-uncertainty = true,
+  bracket-numbers = false,
+  product-units = single,
+  multi-part-units = single,
+}
 \usepackage[version=4]{mhchem}
@@
 
-\aff[a]{Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232 \country{Australia}}
+\aff[a]{ANSTO, Locked Bag 2001, Kirrawee DC, NSW 2232 \country{Australia}}
 \aff[b]{School of Chemical Engineering, University of New South Wales,  Sydney, NSW, 2052 \country{Australia}}
@@
 \newcommand{\Objective}{\textbf{Objective}}
-\newcommand{\CurveFitter}{\textbf{CurveFitter}}
 \newcommand{\GlobalObjective}{\textbf{GlobalObjective}}
@@
 \newcommand{\ReflectModel}{\textbf{ReflectModel}}
+\newcommand{\CurveFitter}{\textbf{CurveFitter}}
 \newcommand{\Spline}{\textbf{Spline}}
@@
 
+\hyphenation{Lipid-Leaflet}
+
 \begin{synopsis}
@@
 
+%TODO en_GB or en_US?
+
 \begin{abstract}
-The \refnx\ package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
+\refnx\ is a model-based neutron and X-ray reflectometry data analysis package written in Python.
+It is cross platform, and has been tested on Linux, macOS, and Windows.
+Its graphical user interface is browser-based, through a \Jupyter\ notebook.
 Model construction is modular, being composed from a series of components that each describe a subset of the interface, parameterised in terms of physically relevant parameters (volume fraction of a polymer, lipid area per molecule, etc).
@@
 Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models.
-Prior knowledge of parameter values is encoded as probability distribution functions or bounds on all parameters in the system.
-Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone.
-Algebraic Parameter constraints are available.
-A choice of fitting approaches is available include least-squares (global and gradient-based optimizers) and a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
+Prior knowledge of parameter values are encoded as probability distribution functions or bounds on all parameters in the system.
+Additional prior probability terms can be defined for sets of components, over and above those available from the parameters alone.
+Algebraic parameter constraints are available.
+A choice of fitting approaches is available, including least-squares (global and gradient-based optimizers) and a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters.
 The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
-The package is designed to facilitate reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits straightforward reproduction of analyses.
+The package is designed to facilitate reproducible research; its use in \Jupyter\ notebooks, and subsequent distribution of those notebooks as supporting information, permits straightforward reproduction of analyses.
 \end{abstract}
@@
 
-The use of specular X-ray and neutron reflectometry for morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has exploded over the past years \cite{Wood2017, Daillant2009}.
+The use of specular X-ray and neutron reflectometry for the morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has grown remarkably over the past years \cite{Wood2017, Daillant2009}.
 Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.
-Several programs are available for this purpose, with a variety of different features \cite{Bjorck2007, Gerelli2016, Kienzle2011, Nelson2006}.
-These programs typically create a model of the interface, and incrementally refine the model against the data using least-squares, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).
+Several programs are available for this purpose, with a variety of different features \cite{Nelson2006,Bjorck2007,Kienzle2011,Gerelli2016}.
+These programs typically create a model of the interface, and either incrementally refine the model against the data using least-squares methods, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H, Kienzle2011} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).
 
-Given that there are more and more publications arising from the reflectometry technique, it is vital that the analysis is reproducible.
-Reproducibility in research is an underlying principle of science.
-Unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
+Given the number of publications arising from the reflectometry technique, it is vital that both the experiments and analyses are reproducible.
+Reproducibility in research is an underlying principle of science; unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses.
 Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions or a codified workflow would need to be provided \cite{Moeller2017a}.
-One example for addressing this reproducibility issue are the guidelines in the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
+One example for addressing this reproducibility issue is the set of guidelines from the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
 
-Here we outline a new reflectometry analysis package, \refnx\ (version number 0.1 is used in this paper \cite{refnx}), that can address the reproducibility issue for the reflectometry community as it is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa} using a Python kernel.\footnote{We do not mean that other programs are irreproducible, rather that the information provided by scientists in journal articles is often lacking.}
-These notebooks are a mix of executable code cells and markup.
-An analysis performed in such a notebook can be appended as supporting information, along with the data, to an article.
-Readers can then replicate the exact data analysis, provided they have set up the same computing environment.
+Here, we outline a new reflectometry analysis package, \refnx\ (version number 0.1 is used in this paper \cite{refnx}), that helps address the reproducibility issue for the reflectometry community\footnote{We do not mean that other programs are irreproducible, rather that the information provided in journal articles is often lacking.} by creating a scripted analysis workflow that is readily published alongside the publication, such as we have done with this paper (see the Supporting Information).
+The \refnx\ Python package is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa}, which provide a literate programming environment that mixes executable code cells, rich documentation of the steps that were performed, and the computational output.
+By including the analysis, as performed by the authors, in such a notebook, and appending it as supporting information along with the data, readers are empowered to replicate the exact data analysis and potentially extend the analysis, provided they have set up the same computing environment\cite{Millman2014}.
 Setting up the computing environment is simplified using the \conda\ package manager \cite{conda}, and an environment file (although other approaches are available).
-To that end the \Jupyter\ notebooks for the example analysis performed in this paper are appended as supporting information.
-
-\refnx\ has a wide range of sophisticated modelling capabilities including: parameter constraints, description of prior probabilities on parameters using arbitrary probability distribution functions, modular construction of models using a variety of components that are user extensible, co-refinement of datasets, handling of patchy layers, a graphical user interface, resolution handling, Markov Chain Monte Carlo sampling of the posterior probability distributions for the parameters, model selection, etc.
-
-The posterior probability distribution for a parameter set in Bayesian statistics, Equation~\ref{eqn:1}, is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities).
-
-\begin{gather} 
-\label{eqn:1}\ p(\theta | D, I) \propto p(\theta | I)\times p(D | \theta, I)\\
-p(D | \theta, I) = -\frac{1}{2} \sum \left[\left(\frac{y_n - model} {\sigma_n}\right)^2 + log(\sigma_n^2)\right]\label{eqn:2}
-\end{gather}
-
-The prior distribution, $p(\theta | I)$, is the probability of a parameter, $\theta$, given preexisting knowledge of the system, $I$.
-For example, a prior could be a simple Uniform distribution that specifies a lower and upper bound, or a normal distribution that represents an experimentally derived value.
-The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information.
-It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $model$.
-
-The posterior distribution, $p(\theta | I, D)$, is the probability of the parameters given the data and prior knowledge about the system.
-The posterior probability is sampled by encoding the likelihood and prior distributions and using Markov Chain Monte Carlo (MCMC) techniques \cite{emcee, ptemcee}.
-At the end of an MCMC run the parameter set possesses a number of samples (called a `chain'), whose statistics reveal the distribution and covariance of the parameters, the spread of the model around the data, and in a reflectometry context the range of structures that are consistent with the data.
 
@@
 
-\refnx\ is written in Python with an object-oriented design, Figure~\ref{fig:components}.
+\refnx\ is written in Python with an extensible object-oriented design, Figure~\ref{fig:components}, in which the user creates a model of the sample based on what they know about its composition, with refinement of that model against the data.
 As with \emph{Motofit} \cite{Nelson2006} it calculates reflectivity using the Abeles method \cite{Heavens1955} for specular reflection from a stratified medium.
-The building block of the analysis is the \Parameter\ object which represents a model value, whether it is allowed to vary in a fit, and a bounds attribute.
-The bounds are a probability distribution representing the prior.
-Any of the \emph{scipy.stats} \cite{Jones2001-2017} continuous distributions, or distributions created by the user, can be used for this purpose.
-Algebraic relationships between \Parameter\ can be applied using constraints.
 
-The \Structure\ object represents the interfacial model, comprising of individual \Component\ objects in series.
-Each \Component\ represents a subset of the interface and contains several physically relevant Parameters.
-The simplest \Component\ is a \Slab\, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
-The simplest models are simply a series of \Slab.
-More sophisticated components include \LipidLeaflet\ and \Spline.
-\Spline\ is designed for freeform modelling of an SLD profile using spline interpolation.
-In addition to its constituent parameters each \Component\ can also contribute to the log-prior probability.
-This is useful when a \Component\ has a derived value, such as surface coverage, which is already known, and can be included as prior knowledge of the system.
-Each \Component\ has a \emph{slabs} property that represents the strata for its particular subset of the interface.
+\begin{figure}
+  \includegraphics[width=85mm]{components.pdf}
+  \caption{Schematic showing the relationship between classes that make up a typical reflectometry curve-fitting problem.
+The key step for the user is assembling materials (\Component) such as a `Slab: Component' (a \Component\ that is a \Slab) and encoding prior knowledge into each \Parameter\ that describes that \Component.}
+  \label{fig:components}
+\end{figure}
+
+The building block of the analysis is the \Parameter\ object which represents a model value (e.g.
+the SLD of the material), whether it is allowed to vary in a fit, and a bounds attribute.
+The bounds are a probability distribution representing pre-existing knowledge of a parameter's value, called a prior probability.
+A prior might be a simple uniform distribution that specifies a lower and upper bound (e.g.
+volume fraction is in the interval $[0, 1]$), or a normal distribution that represents an experimentally derived value and associated uncertainty (e.g.
+thickness is $\SI{100+-4}{\angstrom}$).
+Any of the \emph{scipy.stats} \cite{Jones2001-2017} continuous distributions, or other distributions created by the user, can be used for this purpose.
+Algebraic relationships between \Parameter\ objects can be applied to permit more sophisticated constraints that can cross between \Component\ objects (e.g.
+the sum of the thicknesses of several layers is known to some uncertainty).
+
+\subsection{Structure representation}
+
+The \Structure\ object represents the interfacial model, assembled from individual \Component\ objects in series.
+Each \Component\ represents a subset of the interface and selected attributes of the \Component\ can be described by physically relevant \Parameter\ objects.
+The simplest and most familiar \Component\ is a \Slab, which has a uniform scattering length density (SLD), thickness, roughness, and volume fraction of solvent.
+The simplest models are simply a series of \Slab\ objects.
+More sophisticated components include \LipidLeaflet\ (a lipid monolayer, or one-half of a lipid bilayer) and \Spline\ (for freeform modelling of an SLD profile using spline interpolation).
+It is straightforward to develop/modify new components for different structural functionality, a consequence of the program design.
+
+To include further prior knowledge of the real sample into the model,
+each \Component\ can additionally contribute to the prior probability in addition to its constituent \Parameter\ objects.
+This is useful when a \Component\ has a derived value, such as surface excess, which is already known.
+
+To calculate the reflectivity from series of \Component\ objects that form the model,
+each \Component\ has a \emph{slabs} property that represents a discretised `slice' approximation to a continuous SLD profile for its particular region of the interface.
 A \Slab\ object has a single slice because it is a single thickness of uniform SLD.
-A \LipidLeaflet\ can be made of two slices (head/tail regions), but the \Spline\ Component has many.
-These slices have uniform SLD, and use the Nevot-Croce approach \cite{Nevot1980} to describe roughness between them.
-If a different roughness model is required then a `microsliced' \Component\ could be written to accomodate that.
+A \LipidLeaflet\ is made of two slices (head/tail regions), but the \Spline\ has many thin slices approximating the smooth curve.
+Each of these slices has uniform SLD, with the N\'{e}vot--Croce approach being used to describe the roughness between them \cite{Nevot1980}.
 
 The \Structure\ object is used to construct a \ReflectModel\ object.
-This object is responsible for calculating the resolution smeared reflectivity of the \Structure\, scaling the data, and adding a linear background (via the scale and background Parameters).
-There are different types of smearing available - constant $\mathrm{d}Q/Q$, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
+This object is responsible for calculating the resolution smeared reflectivity of the \Structure, scaling the data, and adding a $Q$-independent constant background (via the scale and background \Parameter\ objects).
+There are different types of smearing available: constant $\mathrm{d}Q/Q$, point-by-point resolution smearing read from the dataset of interest, or via a smearing probability kernel of arbitrary shape \cite{Nelson2014}.
 The constant $\mathrm{d}Q/Q$ and point-by-point smearing use Gaussian convolution, with $\mathrm{d}Q$ representing the full width half maximum (FWHM) of a Gaussian approximation to the instrument resolution function \cite{Well2005}.
 
-The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
+\subsection{Model/data comparison}
+The \Objective\ class is the comparator of the predicted and measured reflectivities, using the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood (Equation~\ref{eqn:2}), log-prior, residuals, and the generative model.
 The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$.
-The \DataD\ object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile.
+As is standard for many reflectometry data files, the \DataD\ object reads a three or four column plain-text datafile.
 A three column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$ (1 standard deviation).
 A four column dataset represents $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}).
-Subclassing \DataD\ would allow other formats to be read.
-One example of this could be an wavelength dispersive file using $\Omega$, $\lambda$ data instead of $Q$; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
+Extending \DataD\ would allow other formats to be read.
+One example of this could be a wavelength dispersive file using ($\Omega$, $\lambda$)-data instead of $Q$, such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers.
 In such a case \ReflectModel\ could be subclassed to make full use of this energy dispersive information.
-An \Objective\ can be given a \Transform\ object to permit fitting as $\log R$ vs $Q$, $RQ^4$ vs $Q$, or $R$ vs $Q$.
-Several \Objective\ can be combined to form a \GlobalObjective\ for co-refinement.
-The object-oriented nature allows \Parameter\, \Component\ to be reused in in different \Objective, thereby facilitating co-refinement.
-%FIXME: above said 'lin-R' is that linear or natural log (\ln)
 
-The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting or Bayesian MCMC of the system.
-\refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters.
-\ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
+An \Objective\ can be given a \Transform\ object to permit fitting as $\log_{10} R$ vs $Q$, $RQ^4$ vs $Q$; the default (no \Transform) is $R$ vs $Q$.
+Several \Objective\ objects can be combined to form a \GlobalObjective\ for co-refinement.
+The object-oriented nature allows \Parameter, \Component\ to be reused in different \Objective, and this is the basis for linking parameters between samples for co-refinement.
+For a comprehensive demonstration of multiple contrast co-refinement, see the annotated notebook in the supporting information.
+
+\subsection{Statistical comparison and model refinement}
+
+The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting with the functionality provided by the \SciPy\ package (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds).
+\CurveFitter\ can also perform Bayesian Markov Chain Monte Carlo (MCMC) sampling of the system, examining the posterior probability distribution of the parameters, Equation~\ref{eqn:1}.
+The posterior distribution is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities):
+%
+\begin{gather} 
+\label{eqn:1}\ p(\theta | D, I) \propto p(\theta | I)\times p(D | \theta, I)\\
+p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(\sigma_n^2)\right]\label{eqn:2}
+\end{gather}
+%
+The prior, $p(\theta | I)$, is the probability distribution function for a parameter, $\theta$, given preexisting knowledge of the system, $I$, as outlined above.
+The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information.
+It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $y_{\mathrm{model},n}$.
 The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
@@
 Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
-Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation.
-Visualisation of the samples produced by MCMC sampling is done using the \corner\ package \cite{corner} for scatter plot matrices.
-On the conclusion of a fit/sampling run each \Parameter\ value is updated and given a standard error.
-For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.
 
-\begin{figure}
-  \includegraphics[width=175mm]{components}
-  \caption{Schematic showing the relationship between classes that make up a typical reflectometry curve-fitting problem.}
-  \label{fig:components}
-\end{figure}
+The posterior probability, $p(\theta | I, D)$, describes the distribution of parameter values consistent with the data and prior information.
+In the simplest form, this is akin to a confidence interval for a parameter derived by least-squares analysis.
+However, when parameters are correlated, or two models give similar quality of fit ('multi-modality'), a simple confidence interval can be misleading.
+%FIXME - confidence intervals not used in Bayesian stats https://en.wikipedia.org/wiki/Credible_interval
+ The posterior probability is derived by encoding the likelihood and prior distributions and then using an MCMC algorithm (via the \emcee\ and \ptemcee\ packages) to perform affine invariant ensemble sampling.\cite{emcee, ptemcee}
+At the end of an MCMC run, the parameter set possesses a number of samples (called a `chain'); the samples reveal the distribution and covariance of the parameters, the spread of the model-predicted measurements around the data, and in a reflectometry context, the range of SLD profiles that are consistent with the data.
+%FIXME the samples are not similarly plausible. 
+The chain statistics are used to update each \Parameter\ value, and assign a standard error.
+For the sampling, these represent the median and half the $[15.87, 84.13]$ percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.
 
-To make it easy to create quick models, and to ease the learning curve, an ipywidgets \cite{ipywidgets} based fitting graphical user interface (GUI) can be created in a \Jupyter\ notebook, Figure~\ref{fig:gui}.
-This GUI builds slab based models for analysing a single dataset, but can be used as a stepping point for building more advanced models via the `To code' code generation button.
-A fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
-For a comprehensive demonstration of multiple contrast co-refinement see the annotated notebook in the supporting information.
+The \ptemcee\ package is a variant (a `fork' in open-source software development terms) of the \emcee\ package that has been extended to implement the parallel tempering algorithm for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher `temperatures', while individual modes are efficiently explored by chains at lower `temperatures' \cite{ptemcee}.
+Having multiple populations in the parallel tempering algorithm allows the sampler to escape local maxima, greatly aiding it's ability to explore the most probable regions of the posterior.
+
+Parallelisation of the sampling is automatic, making full use of multi-core machines, and can use MPI on a cluster for yet greater parallelisation.
+Visualisation of the samples produced by MCMC sampling is performed using the \corner\ package for scatter plot matrices \cite{corner}, which gives a representation of the probability distribution function for each individual parameter and also the covariance for each pair of parameters.
+As will be seen later, the plot for two normally distributed and uncorrelated parameters is isotropic, while covariant parameters show significant anisotropy.
+An evaluation of the impact of hard bounds can also be made by looking for plots where the bounds are clearly truncating the distribution function, allowing the bounds to be re-evaluated and adjusted if necessary.
+
+\subsection{User interface}
+
+A significant motivation in the development of \refnx\ has been the facilitation of reproducible analysis by helping the user describe \emph{how} the analysis was performed.
+A few lines of computer code is an incredibly powerful description, conveying the details with precision that is hard to match in written text, as well as being incredibly concise.
+%FIXME this line seems redundant.
+%Analysis code can be constructed in \refnx\ in relatively few lines of code (as illustrated in the supporting information), with example analyses often being sufficient to complete the task.
+These few lines of Python code can be further extended to produce publication quality plots saved and ready to import into the next publication.
+
+While Python is a popular language for instruction and for data analysis, meaning that the relatively few lines of code required to complete a \refnx\ analysis of a set of experiments is not a huge hurdle, a simpler graphical user interface (GUI) is also provided.
+The browser-based GUI is available for fitting within a \Jupyter\ notebook, Figure~\ref{fig:gui}, leveraging the \ipywidgets\ modules \cite{ipywidgets}.
+The GUI has a `To code' button that turns the current model into the few lines of code required to perform the analysis without using the GUI, thus providing the desired instructions for the reproducible analysis.
+The ability to generate analysis code allows also makes it a stepping point for building more advanced models independently.
+The current GUI is able to use slab based models for fitting a single dataset; a fully functional web-based reflectometry analysis notebook is currently available \cite{Nelson2018}.
 
@@
   \includegraphics[width=85mm]{./supporting_information/gui.png}
-  \caption{Screenshot of the \Jupyter/\ipywidgets\ GUI. \Jupyter\ notebook available in supporting information.}
+  \caption{Screenshot of the \Jupyter/\ipywidgets\ GUI; this \Jupyter\ notebook is available in the supporting information.}
   \label{fig:gui}
@@
 
-\subsection{Example}
+\section{Example data analysis with a lipid bilayer}
 
@@
 Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information in the scattering experiment) and improve the ability to determine the structure of various components in the system.
-The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule.
+The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as the area per molecule \cite{campbell2018}.
 Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas.
-\refnx\ has functionality for all these requirements, such as the \LipidLeaflet\ component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel.
-It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach.
+\refnx\ has functionality for all these requirements, such as the \LipidLeaflet\ component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel\ to account for patchiness.
 
-The parameters used in the \LipidLeaflet\ component are: area per molecule ($A$), thicknesses for each of the head and tail regions ($t_x$), sums of scattering lengths of the head and tail regions ($b_x$), partial volumes of the head and tail groups ($V_x$), roughness between head and tail region, and SLDs of the solvents for the head and tail group ($\rho_{x, solv}$).
-The overall SLD of each of the head and tail group regions are given by Equations~\ref{eqn:3} and \ref{eqn:4}.
-The approach used in this component ensures that there is a 1:1 correspondence of heads to tails.
-%TODO cite a paper which gives a whole load of volumes?
+The parameters used in the \LipidLeaflet\ component are: area per molecule ($A$), thicknesses for each of the head and tail regions ($t_x$), sums of scattering lengths of the head and tail regions ($b_x$), partial volumes of the head and tail groups ($V_x$), roughness between head and tail region, and SLDs of the solvents for the head and tail group ($\rho_{x,\mathrm{solv}}$).
+The overall SLD of each of the head and tail group regions are given by:
 \begin{gather} 
 \label{eqn:3} \phi_{x} = \frac{V_x}{At_x}\\
-\rho_x =  \phi_{x} \frac{b_x}{V_x} + (1 - \phi_{x})\rho_{x, solv} \label{eqn:4}
+\rho_x =  \phi_{x} \frac{b_x}{V_x} + (1 - \phi_{x})\rho_{x,\mathrm{solv}} \label{eqn:4}
 \end{gather}
-
+The approach used in \LipidLeaflet\ component ensures that there is a 1:1 correspondence of heads to tails.
 By default the head and tail solvents are assumed to be the same as the solvent that is used throughout the \Structure.
@@
 
-Here \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=\SI{2.07E-6}{\per\square\angstrom}], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phospho\-choline (DMPC) bilayer at the solid-liquid interface, Figure~\ref{fig:global_fit}.\footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.} Two \LipidLeaflet\ are required to describe the inner and outer leaflets of a bilayer, the component contains an attribute which can reverse the direction of one of the leaflets.
+Here, \LipidLeaflet\ is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=\SI{2.07E-6}{\per\square\angstrom}], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phospho\-choline (DMPC) bilayer at the solid-liquid interface, Figure~\ref{fig:global_fit}.\footnote{The validity of \LipidLeaflet\ does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.} Two \LipidLeaflet\ objects are required to describe the inner and outer leaflets of a bilayer, hence, the component contains an attribute which can reverse the direction of one of the leaflets.
 The use of individual objects to describe each leaflet leads to great flexibility; it becomes easy to model asymmetric bilayers (inner leaflet can be a different lipid to the outer lipid), and one can model interstitial water layers between the leaflets as well.
@@
 The corner plot (Figure~\ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of \SI{57.0 \pm0.15}{\square\angstrom}.
-Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile.
-These are obtained by random samples from the MCMC chain.
+Figure~\ref{fig:global_fit} shows the probability distribution of the generative model around the data and in the SLD profile.
+These families of plausible fits that are obtained by plotting a subset of samples from the MCMC chain.
 The spread in SLD profiles is used to determine what range of structures is consistent with the data.
-Multi-modalities in these SLD profiles can be due to statistical uncertainties, the Q ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
-%TODO A reference for V_m?
-%FIXME units of area per molecule were wrong; check
+Multi-modalities in these SLD profiles can be due to statistical uncertainties, the $Q$ ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
 
-\begin{figure}%
+\begin{figure}
 \centering
 \label{fig:global_fit}%
-\includegraphics[width=85mm]{./supporting_information/global_fit.png}%
-\label{fig:d2o_sld_spread}%
-\includegraphics[width=85mm]{./supporting_information/d2o_sld_spread.png}
-\caption{a) Reflectivity from a DMPC bilayer measured at three contrasts, with median in red, and 500 samples from the posterior distribution.
-Dataset for \ce{Si} match offset by 0.1, \ce{H_2O} contrast offset by 0.001.
-b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median.}
+\includegraphics[width=85mm]{./supporting_information/global_fit.pdf}%
+%TODO: series labels on plots; delete points?;
+%FIXME: not clear what you mean by the above two points.
+
+%FIXME: artefact in high q d2o fit; truncate at Q = 0/35 - I truncated the data at 0.3.
+%FIXME: h2o fit isn't great about 0.20 - tried lots of things to improve this (including patchiness), nothing seems to work
+
+\includegraphics[width=85mm]{./supporting_information/d2o_sld_spread.pdf}
+
+%TODO add (a) and (b)
+%FIXME - where should I add (a) and (b), on the graph?
+\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red.
+Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.001 respectively.
+b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red.
+It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=175mm]{./supporting_information/corner.png}
-  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts.
-The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
+  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
+  \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts.
+The sampling took $\sim$\SI{13}{\minute} on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.
+A larger scale image is available in supporting information.}
   \label{fig:corner}
@@
 In addition, there is a benchmarking suite to track changes in performance, specifically the speed of critical calculations, over time.
+This development approach is important to providing assurances to the community that the code is tested and works.
 
-The source code for \refnx\ is held in a version controlled git repository hosted on github at https://www.github.com/refnx/refnx.
-Contributors create their own fork of the main \refnx\ repository, and create a feature branch to which they make modifications.
+The source code for \refnx\ is held in a publicly accessible version controlled git repository\cite{refnx}.
+The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications.
 They then submit a pull request (PR) against the main repository.
-The modifications made in the PR are checked on continuous integration (CI) web-services which run the test suite against a matrix of Python versions on the macOS, Linux and Windows operating systems.
-If the tests pass, and the changes are considered useful, then the features are merged into the main repository.
-When a sufficient number of features have accumulated a new release is made.
-Successive releases have an incrementing semantic version number which can be obtained from the installed package, with each release being given its own DOI.
+The modifications made in the PR are checked on continuous integration (CI) web-services that run the test suite against a matrix of Python versions on the macOS, Linux and Windows operating systems.
+Features are merged into the main repository if all tests pass, and if manual code review concludes that the changes are scientifically correct, of sufficiently high standard, and useful.
+When a sufficient number of features have accumulated, a new release is made.
+Successive releases have an incrementing semantic version number which can be obtained from the installed package, with each release being given its own Digital Object Identifier (DOI).
 
@@
 These distributables are made as part of the release process using the same CI web-services used to test the code.
-The matrix of distributables cover the major Python versions currently in use, across the macOS, Windows, and Linux operating systems.
-Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI.
-\footnote{https://pypi.python.org/pypi/refnx} Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.
+The matrix of distributables covers the major Python versions currently in use, across the macOS, Windows, and Linux operating systems.
+Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI.\footnote{https://pypi.python.org/pypi/refnx; the installation command is `\texttt{pip install refnx}'} Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed; further dependencies should be installed to run the test suite to verify that compilation and installation was successful.
 
-\refnx\ is released under the BSD permissive open source licence. In addition its dependencies are released under open source licences which mean that use is free of cost to the end user.
+\refnx\ is released under the BSD permissive open source licence.
+In addition, all of the  dependencies of \refnx\ are released under open source licences which means that use is free of cost to the end user and, more importantly, the user user is free to modify, improve, and inspect this software.
 
@@
 
-In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
+In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met:
 \begin{itemize}
-  \item the datasets used need to be deposited with a journal article, or be freely available.
+  \item the processed datasets used in the analysis need to be deposited with a journal article, or be freely available.
+Ideally the raw datasets, and the means to create the processed datasets should also be made available.
   \item the exact software environment needs to be recreatable.
@@
 Each of these points are often omitted in the literature.
-For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
-Whilst it is unable to meet the first criteria by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken.
+For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user.
+Whilst it is unable to meet the first criterion by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken.
+As we have already noted, the ordered set of steps to perform the analysis is the \Jupyter\ notebook in which the analysis was performed and this is an artefact able to be archived.
+
 The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc).
@@
 \conda\ can use environment files to recreate a specific setup.
-An alternative way of recreating the environment is by using a virtual machine, such as Docker.
-The ordered set of steps to perform the analysis is recordable in the \Jupyter\ notebook.
+An alternative way of recreating the environment is by using a virtual machine, or other container environment such as Docker; the strengths and weaknesses of various software distribution practices and the relationship with reproducible science has been discussed in detail elsewhere \cite{Moeller2017a}.
+
 The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here.
-With closed source or proprietary software the ability to return to a specific software version/environment can be difficult, different versions can have modifications that can change the output of an analysis.
-In addition accessibility (due to cost, etc) to the wider scientific community can also hinder reproducibility.
+With closed source or proprietary software, the ability to return to a specific software version/environment can be frustrated, and different versions can have modifications that can unknowingly change the output of an analysis.
+In addition reduced accessibility (due to cost, etc) to the wider scientific community can also hinder reproducibility.
+
 Moreover, there are important ramifications for verifiability.
@@
 Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.
+%include citation
+%FIXME: this is a hypothesis, without being able to see the testing practices and codebases of proprietary programs it's hard to tell.
+However, given that open source software has bugs, it's safe to say that these will also occur in proprietary programs.
 
@@
 
-\refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and with extensibility in mind.
-Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, algebraic inter-parameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a (\Jupyter\ ) \ipywidgets\ GUI.
+\refnx\ is a powerful tool for least-squares or Bayesian analysis of neutron and X-ray reflectometry data that is ideally usable for reproducible research with \Jupyter\ notebooks, and has been built with extensibility in mind.
+Its features include: MCMC sampling of posterior distribution for parameters, structural models constructed from modular components with physically relevant parameterisation, algebraic inter-parameter constraints, mixed area models, co-refinement of multiple datasets, probability distributions for parameter bounds used directly for log-prior terms, and a (\Jupyter) \ipywidgets\ GUI.
 
@@
 \textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
+\textbf{corner.pdf} - larger scale image of the corner plot.\\
+\textbf{c\_PLP0016596.dat}, \textbf{c\_PLP0016601.dat}, \textbf{c\_PLP0016607.dat} - example lipid datasets.\\
+\textbf{reduction.ipynb} - notebook for reducing example datasets.\\
+\textbf{raw\_data.zip} - raw files for the example datasets.\\
 \textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.

### 2018-08-02 paper/manuscript.tex
PAPER: model evidence

@@
 \begin{gather} 
-\label{eqn:1}\ p(\theta | D, I) \propto p(\theta | I)\times p(D | \theta, I)\\
+\label{eqn:1}\ p(\theta | D, I) = \frac{p(\theta | I)\times p(D | \theta, I)}{p(D | I)}\\
 p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(\sigma_n^2)\right]\label{eqn:2}
@@
 %
-The prior, $p(\theta | I)$, is the probability distribution function for a parameter, $\theta$, given preexisting knowledge of the system, $I$, as outlined above.
+The prior, $p(\theta | I)$, is the probability distribution function for a parameter, $\theta$, given pre-existing knowledge of the system, $I$, as outlined above.
 The likelihood (Equation~\ref{eqn:2}), $p(D | \theta, I)$, is the probability of the observed data, $D$, given the model parameters and other prior information.
 It is calculated from the measured data, $y_n$ (with uncertainties $\sigma_n$), and the generative model, $y_{\mathrm{model},n}$.
-The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}.
-However, other types of measurement errors (e.g.
+The likelihoods that are used here assume that the measurement uncertainties are normally distributed, Equation~\ref{eqn:2}.
+However, other types of measurement uncertainties (e.g.
 Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
+The model evidence, $p(D | I)$, is a normalising factor.
 
@@
 %FIXME the samples are not similarly plausible. 
-The chain statistics are used to update each \Parameter\ value, and assign a standard error.
+The chain statistics are used to update each \Parameter\ value, and assign a standard uncertainty.
 For the sampling, these represent the median and half the $[15.87, 84.13]$ percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.
@@
 Having multiple populations in the parallel tempering algorithm allows the sampler to escape local maxima, greatly aiding it's ability to explore the most probable regions of the posterior.
+\ptemcee\ is also able to estimate the log-evidence term (the denominator in Equation~\ref{eqn:2}), which is useful when calculating the Bayes factor for model comparison.
+%FIXME: reference for model selection...
 

### 2018-08-10 paper/manuscript.tex
PAPER: include autocorrelation plot in notebook;

@@
   \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts.
-The sampling took $\sim$\SI{13}{\minute} on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.
+The sampling took $\sim$\SI{41}{\minute} on a \SI{2.8}{GHz} quad-core computer for 16 saved steps, corresponding to 4800 samples, with the steps being thinned by a factor of 500.
 A larger scale image is available in supporting information.}

### 2018-08-13 paper/manuscript.tex
PAPER: add another reference
PAPER: rejigged figure

@@
 Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.
-Several programs are available for this purpose, with a variety of different features \cite{Nelson2006,Bjorck2007,Kienzle2011,Gerelli2016}.
+Several programs are available for this purpose, with a variety of different features \cite{Nelson2006,Bjorck2007,Kienzle2011,Gerelli2016,Hughes2016}.
 These programs typically create a model of the interface, and either incrementally refine the model against the data using least-squares methods, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H, Kienzle2011} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).
@@
 \includegraphics[width=85mm]{./supporting_information/global_fit.pdf}%
-%TODO: series labels on plots; delete points?;
-%FIXME: not clear what you mean by the above two points.
-
-%FIXME: artefact in high q d2o fit; truncate at Q = 0/35 - I truncated the data at 0.3.
-%FIXME: h2o fit isn't great about 0.20 - tried lots of things to improve this (including patchiness), nothing seems to work
 
@@
 
-%TODO add (a) and (b)
-%FIXME - where should I add (a) and (b), on the graph?
 \caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red.
-Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.001 respectively.
+Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.01 respectively.
 b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red.
@@
   \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts.
-The sampling took $\sim$\SI{41}{\minute} on a \SI{2.8}{GHz} quad-core computer for 16 saved steps, corresponding to 4800 samples, with the steps being thinned by a factor of 500.
+The sampling took $\sim$\SI{33}{\minute} on a \SI{2.8}{GHz} quad-core computer for 20 saved steps, corresponding to 4000 samples, with the steps being thinned by a factor of 400.
 A larger scale image is available in supporting information.}

### 2018-08-13 paper/manuscript.tex
Fix bibliography for iucr
- Use a vendored version of iucr.bst if available
  iucr.bst doesn't actually match the instructions to authors
- Fix various parts of .bib file so that it is rendered correctly
- Fix data in .bib file
Add extra refs

@@
 \journalcode{J}
+
+% \usepackage[colorlinks,urlcolor=black]{hyperref}
+\renewcommand{\harvardurl}[1]{\url{#1}}
+\newcommand{\url}[1]{#1}
 
@@
 
-In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met:
+In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met \cite{Helliwell2017, Moeller2017a}:
 \begin{itemize}
@@
 \end{itemize} 
-Each of these points are often omitted in the literature.
-For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user.
+Each of these points is often inadequately addressed in the literature.
+For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user \cite{Chirigati2013}.
 Whilst it is unable to meet the first criterion by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken.
@@
 
-The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here.
+The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here \cite{Moeller2017a}.
 With closed source or proprietary software, the ability to return to a specific software version/environment can be frustrated, and different versions can have modifications that can unknowingly change the output of an analysis.
@@
 
-Moreover, there are important ramifications for verifiability.
+Moreover, there are important ramifications for verifiability \cite{Chirigati2013}.
 \refnx\ is based on a fully open software stack, with good unit test coverage.
@@
 Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.
-%include citation
-%FIXME: this is a hypothesis, without being able to see the testing practices and codebases of proprietary programs it's hard to tell.
-However, given that open source software has bugs, it's safe to say that these will also occur in proprietary programs.
 
@@
 \bibliography{main}{}
+
+% the provided iucr.bst doesn't match the journal style but a fixed version
+% is not redistributable.
+\IfFileExists{iucrdoi.bst}{
+  \bibliographystyle{iucrdoi}
+}{
   \bibliographystyle{iucr}
+}
 \end{document}

### 2018-08-13 paper/manuscript.tex
Updates from discussion

@@
 Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models.
-Prior knowledge of parameter values are encoded as probability distribution functions or bounds on all parameters in the system.
+Prior knowledge of parameter values is encoded as probability distribution functions or bounds on all parameters in the system.
 Additional prior probability terms can be defined for sets of components, over and above those available from the parameters alone.
@@
 The \refnx\ Python package is specifically designed for use in \Jupyter\ notebooks \cite{Kluyver:2016aa}, which provide a literate programming environment that mixes executable code cells, rich documentation of the steps that were performed, and the computational output.
-By including the analysis, as performed by the authors, in such a notebook, and appending it as supporting information along with the data, readers are empowered to replicate the exact data analysis and potentially extend the analysis, provided they have set up the same computing environment\cite{Millman2014}.
+By including the analysis, as performed by the authors, in such a notebook, and appending it as supporting information along with the data, readers are empowered to replicate the exact data analysis and potentially extend the analysis, provided they have set up the same computing environment \cite{Millman2014}.
 Setting up the computing environment is simplified using the \conda\ package manager \cite{conda}, and an environment file (although other approaches are available).
@@
 As with \emph{Motofit} \cite{Nelson2006} it calculates reflectivity using the Abeles method \cite{Heavens1955} for specular reflection from a stratified medium.
+Detailed documentation for \refnx\ is available on-line\footnote{https://refnx.readthedocs.io/} and is distributed with the package.
 
@@
 The \Objective\ class is the comparator of the predicted and measured reflectivities, using the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood (Equation~\ref{eqn:2}), log-prior, residuals, and the generative model.
-The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$.
+The \DataD\ object has \emph{x, x\_err, y, y\_err} attributes to represent $Q$, $\mathrm{d}Q$, $R$, $\mathrm{d}R$.
 As is standard for many reflectometry data files, the \DataD\ object reads a three or four column plain-text datafile.
 A three column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$ (1 standard deviation).
-A four column dataset represents $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}).
+A four column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}).
 Extending \DataD\ would allow other formats to be read.
@@
 Several \Objective\ objects can be combined to form a \GlobalObjective\ for co-refinement.
-The object-oriented nature allows \Parameter, \Component\ to be reused in different \Objective, and this is the basis for linking parameters between samples for co-refinement.
+The object-oriented nature allows reuse of \Parameter and \Component\ objects, and this is the basis for linking parameters between samples for co-refinement.
 For a comprehensive demonstration of multiple contrast co-refinement, see the annotated notebook in the supporting information.
@@
 In the simplest form, this is akin to a confidence interval for a parameter derived by least-squares analysis.
-However, when parameters are correlated, or two models give similar quality of fit ('multi-modality'), a simple confidence interval can be misleading.
-%FIXME - confidence intervals not used in Bayesian stats https://en.wikipedia.org/wiki/Credible_interval
- The posterior probability is derived by encoding the likelihood and prior distributions and then using an MCMC algorithm (via the \emcee\ and \ptemcee\ packages) to perform affine invariant ensemble sampling.\cite{emcee, ptemcee}
+However, when parameters are correlated, or two models give similar quality of fit (`multi-modality'), a simple confidence interval can be misleading.
+The posterior probability is derived by encoding the likelihood and prior distributions and then using an MCMC algorithm (via the \emcee\ and \ptemcee\ packages) to perform affine invariant ensemble sampling \cite{emcee, ptemcee}.
 At the end of an MCMC run, the parameter set possesses a number of samples (called a `chain'); the samples reveal the distribution and covariance of the parameters, the spread of the model-predicted measurements around the data, and in a reflectometry context, the range of SLD profiles that are consistent with the data.
-%FIXME the samples are not similarly plausible. 
 The chain statistics are used to update each \Parameter\ value, and assign a standard uncertainty.
@@
 A few lines of computer code is an incredibly powerful description, conveying the details with precision that is hard to match in written text, as well as being incredibly concise.
-%FIXME this line seems redundant.
-%Analysis code can be constructed in \refnx\ in relatively few lines of code (as illustrated in the supporting information), with example analyses often being sufficient to complete the task.
+Example analyses within the \refnx\ code base are often sufficient to complete the task.
 These few lines of Python code can be further extended to produce publication quality plots saved and ready to import into the next publication.
@@
 
-The source code for \refnx\ is held in a publicly accessible version controlled git repository\cite{refnx}.
+The source code for \refnx\ is held in a publicly accessible version controlled git repository \cite{refnx}.
 The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications.
@@
 
-\bibliography{main}{}
+\bibliography{main}
 

### 2018-08-13 paper/manuscript.tex
spell check

@@
 The simplest models are simply a series of \Slab\ objects.
-More sophisticated components include \LipidLeaflet\ (a lipid monolayer, or one-half of a lipid bilayer) and \Spline\ (for freeform modelling of an SLD profile using spline interpolation).
+More sophisticated components include \LipidLeaflet\ (a lipid monolayer, or one-half of a lipid bilayer) and \Spline\ (for free-form modelling of an SLD profile using spline interpolation).
 It is straightforward to develop/modify new components for different structural functionality, a consequence of the program design.
@@
 \ptemcee\ is also able to estimate the log-evidence term (the denominator in Equation~\ref{eqn:2}), which is useful when calculating the Bayes factor for model comparison.
-%FIXME: reference for model selection...
 

### 2018-08-13 paper/manuscript.tex
Add synopsis
tidy caption

@@
 \begin{synopsis}
-%TODO synopsis for ToC
+The refnx Python modules for neutron and X-ray reflectometry data analysis are
+introduced. An sample analysis illustrates a Bayesian approach using a
+Markov Chain Monte Carlo algorithm to understand the confidence in the fit parameters.
 \end{synopsis}
-
-%TODO en_GB or en_US?
 
@@
 \caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red.
-Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.01 respectively.
-b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red.
+Data for the contrast matched (HD\textsubscript{mix}) and \ce{H2O} contrast offset by 0.1 and 0.01 respectively.
+b) SLD profile of the \ce{D2O} model showing 500 samples from the posterior distribution, as well as the median in red.
 It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}

### 2018-08-14 paper/manuscript.tex
PAPER: minor mod to final paragraph

@@
 If problems are discovered, they can be corrected.
-With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors; one has to rely on trust.
-Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.
+With a fully or partially closed-source program such checking is much harder, as one does not possess full knowledge of what happens inside.
 

### 2018-08-14 paper/manuscript.tex
PAPER: 2pi in logl
PAPER: differential evolution space

@@
 
-The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting with the functionality provided by the \SciPy\ package (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds).
+The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting with the functionality provided by the \SciPy\ package (Differential  Evolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds).
 \CurveFitter\ can also perform Bayesian Markov Chain Monte Carlo (MCMC) sampling of the system, examining the posterior probability distribution of the parameters, Equation~\ref{eqn:1}.
@@
 \label{eqn:1}\ p(\theta | D, I) = \frac{p(\theta | I)\times p(D | \theta, I)}{p(D | I)}\\
-p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(\sigma_n^2)\right]\label{eqn:2}
+p(D | \theta, I) = -\frac{1}{2} \sum_n \left[\left(\frac{y_n - y_{\mathrm{model},n}} {\sigma_n}\right)^2 + \log(2\pi\sigma_n^2)\right]\label{eqn:2}
 \end{gather}

### 2018-10-30 paper/manuscript.tex
PAPER: begin changes requested by referee

@@
 Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions or a codified workflow would need to be provided \cite{Moeller2017a}.
-One example for addressing this reproducibility issue is the set of guidelines from the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.
+One example for addressing this reproducibility issue is the set of guidelines from the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010, pauw2013}.
 
@@
 
-The posterior probability, $p(\theta | I, D)$, describes the distribution of parameter values consistent with the data and prior information.
+The posterior probability, $p(\theta | D, I)$, describes the distribution of parameter values consistent with the data and prior information.
 In the simplest form, this is akin to a confidence interval for a parameter derived by least-squares analysis.
@@
 \refnx\ is released under the BSD permissive open source licence.
-In addition, all of the  dependencies of \refnx\ are released under open source licences which means that use is free of cost to the end user and, more importantly, the user user is free to modify, improve, and inspect this software.
+In addition, all of the  dependencies of \refnx\ are released under open source licences which means that use is free of cost to the end user and, more importantly, the user is free to modify, improve, and inspect this software.
 

### 2018-10-30 paper/reply.tex
PAPER: begin changes requested by referee

\documentclass[fontsize=12pt, paper=a4]{scrlttr2}

% Dont forget to read the KOMA-Script documentation, scrguien.pdf

\setkomavar{fromname}{Andrew Nelson} % your name
\setkomavar{fromaddress}{ANSTO \\ Locked Bag 2001 \\ Kirrawee DC \\ NSW 2232 \\ Australia}

\setkomavar{signature}{} % printed after the \closing
\renewcommand{\raggedsignature}{\raggedright} % make the signature ragged right

\setkomavar{subject}{RG5158 - refnx -- Neutron and X-ray reflectometry analysis in Python} % subject of the letter

\begin{document}
\begin{letter}{Dr Gilles Renaud \\ gilles.renaud@cea.fr}

\opening{Dear Dr Renaud}  % eg. Hello
Thank you for forwarding the kind comments of the referees towards my recently submitted manuscript (\#RG5158). I note that they were universally positive, with only minor adjustments to be made. These adjustments towards each referees comments are listed below, and I trust that they meet the requirements for publication in the \emph{Journal of Applied Crystallography}.

\textbf{referee 1}

\textbf{referee 2}
\begin{itemize}
\item \textbf{Resolve the question marks in the Sivia and Skilling reference} These references are completed successfully in our rendering of the latex document. I am unsure why they are not rendered properly by the submission gateway.
\item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
\item \textbf{Third-to-last line – shouldn't this read as p(&thetav;|D,I) instead of p(&thetav;|I,D)?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
\end{itemize}

\textbf{referee 3}
No amendments are required.

\textbf{referee 4}
\begin{itemize}
\item \textbf{Missing references in 1-Introduction (after Sivia 2006)?} These references are completed successfully in our rendering of the latex document. I am unsure why they are not rendered properly by the submission gateway.
\item \textbf{Pauw et al may be added to the references list} This reference has been added.
\item \textbf{please complete the reference Nelson, A and Dewhurst C 2014 46 1338-1346} This reference has been completed.
\end{itemize}

\closing{Regards, \\ Dr Andrew Nelson} %eg. Regards

\end{letter}
\end{document}

### 2018-10-30 paper/manuscript.tex
PAPER: further referee amendments

@@
 The source code for \refnx\ is held in a publicly accessible version controlled git repository \cite{refnx}.
-The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications.
+The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications (such as the addition of a user defined \Component}).
 They then submit a pull request (PR) against the main repository.

### 2018-10-30 paper/reply.tex
PAPER: further referee amendments

@@
 \textbf{referee 1}
+\begin{itemize}
+\item \textbf{How modular is the framework - is it simple for example to extend to include other minimisers?} Additional minimizers from the scipy library can be added relatively simply.
+Without further code modification it's not possible for the CurveFitter machinery to use other minimisers, but such changes could be made if necessary.
+An alternative approach is to use an Objective directly with another minimiser framework.
+\item \textbf{Is there a library of standard models / a way envisaged to allow users to contribute models in a manner similar to the model market place in SASView?} The \emph{LipidLeaflet} component described in the paper could be considered an example of such a model.
+Such components are found in the 'examples' folder of the repository.
+Contribution of user supplied models is welcomed, with the contribution method outlined in the \emph{Distribution and Modification} section: "The standard GitHub workflow is followed in which contributors create their own `fork' of the main refnx repository, and create a feature branch to which they make modifications (such as the addition of a user defined \emph{Component})".
+The authors do not have the resources to host a separate webpage for this purpose, we believe github is usable for this purpose already.
+\item \textbf{Can the fitting run in a headless mode - for multiple batch fitting of data sets?} A headless system is a computer that has been configured to operate without a monitor.
+The refnx package can be used from a Python interpreter in many different ways including (but not limited to): a Jupyter notebook (for browser based interaction), a command line interpreter in a terminal session, a script which the user submits to a cluster (possibly using MPI for parallelisation), etc.
+This list is not exhaustive, but none of those items would require the computer running the interpreter to possess a monitor.
+There is no code within refnx for batch fitting \emph{per se}, but users with a rudimentary understanding of Python (such as that needed to create a model) should be able to create a script to do batch analyses.
+This batch script could be run on any computer capable of running a Python interpreter with the refnx package installed.
+\item \textbf{What is the data format read by the framework does it include metadata from the experiment that is useful for data curation?} The data format that refnx reads is described in detail on page 6 in section 2.2, "Model/Data comparison".
+User provided data arrays can also be used to create the Data1D objects used in the modelling framework.
+No attempt is made to read metadata from the datafile.
+There is currently no standard way of describing a neutron or X-ray reflectometry dataset, each facility has their own methods of including metadata making it difficult to write a universal reader.
+This would be a good community development project for the future.
+\item \textbf{How is the resolution of the instrument accounted for - are geometric instrument parameters scraped from the data file?} The resolution smearing of an instrument is described in detail at the top of page 6 when the \textbf{ReflectModel} is described.
+Constant dq/q or point by point dq/q resolution smearing can be used (Gaussian approximation), with the latter information being read from the 4th column of the dataset, this is also described in the manuscript.
+The manuscript also mentions that a resolution kernel of arbitrary shape can be used.
+However, it's not within the scope of the manuscript to describe the full mathematical detail of how those operations are performed.
+Besides the fourth column of the dataset (dq, if present) no other geometrical information is scraped from the datafile.
+This is because the inclusion of resolution information from various facilities is haphazard, and there is no standard dataset format.
+
+\end{itemize}
 
@@
 \item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
-\item \textbf{Third-to-last line – shouldn't this read as p(&thetav;|D,I) instead of p(&thetav;|I,D)?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
+\item \textbf{Third-to-last line – shouldn't this read as $p(\theta|D,I)$ instead of $p(\theta|I,D)$?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
 \end{itemize}

### 2018-10-30 paper/manuscript.tex
Fix tex error

--- 2018-10-30 paper/manuscript.tex
@@
 The source code for \refnx\ is held in a publicly accessible version controlled git repository \cite{refnx}.
-The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications.
+The standard GitHub workflow is followed in which contributors create their own `fork' of the main \refnx\ repository, and create a feature branch to which they make modifications (such as the addition of a user defined \Component).
 They then submit a pull request (PR) against the main repository.

### 2018-10-30 paper/reply.tex
Use plural (we) in response

@@
 \opening{Dear Dr Renaud}  % eg. Hello
-Thank you for forwarding the kind comments of the referees towards my recently submitted manuscript (\#RG5158).
-I note that they were universally positive, with only minor adjustments to be made.
-These adjustments towards each referees comments are listed below, and I trust that they meet the requirements for publication in the \emph{Journal of Applied Crystallography}.
+Thank you for forwarding the kind comments of the referees towards our recently submitted manuscript (\#RG5158).
+We note that they were universally positive, with only minor adjustments to be made.
+These adjustments towards each referees comments are listed below, and we trust that they meet the requirements for publication in the \emph{Journal of Applied Crystallography}.
 
@@
 \item \textbf{Resolve the question marks in the Sivia and Skilling reference} These references are completed successfully in our rendering of the latex document.
-I am unsure why they are not rendered properly by the submission gateway.
+We are unsure why they are not rendered properly by the submission gateway.
 \item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
@@
 \begin{itemize}
-\item \textbf{Missing references in 1-Introduction (after Sivia 2006)?} These references are completed successfully in our rendering of the latex document.
-I am unsure why they are not rendered properly by the submission gateway.
+\item \textbf{Missing references in 1-Introduction (after Sivia 2006)?} These references are completed successfully in our rendering of the \LaTeX{} document.
+We are unsure why they are not rendered properly by the submission gateway.
 \item \textbf{Pauw et al may be added to the references list} This reference has been added.

### 2018-10-30 paper/reply.tex
Format referee comments separately
Fix file EOL
Fix tex bits

@@
 
-\textbf{referee 1}
+\vskip12pt
+\noindent
+\textbf{Referee 1}
 \begin{itemize}
@@
 Such components are found in the 'examples' folder of the repository.
-Contribution of user supplied models is welcomed, with the contribution method outlined in the \emph{Distribution and Modification} section: "The standard GitHub workflow is followed in which contributors create their own `fork' of the main refnx repository, and create a feature branch to which they make modifications (such as the addition of a user defined \emph{Component})".
+Contribution of user supplied models is welcomed, with the contribution method outlined in the \emph{Distribution and Modification} section: ``The standard GitHub workflow is followed in which contributors create their own `fork' of the main refnx repository, and create a feature branch to which they make modifications (such as the addition of a user defined \emph{Component})".
 The authors do not have the resources to host a separate webpage for this purpose, we believe github is usable for this purpose already.
@@
 This batch script could be run on any computer capable of running a Python interpreter with the refnx package installed.
-\item \textbf{What is the data format read by the framework does it include metadata from the experiment that is useful for data curation?} The data format that refnx reads is described in detail on page 6 in section 2.2, "Model/Data comparison".
+\item \textbf{What is the data format read by the framework does it include metadata from the experiment that is useful for data curation?} The data format that refnx reads is described in detail on page 6 in section 2.2, ``Model/Data comparison".
 User provided data arrays can also be used to create the Data1D objects used in the modelling framework.
@@
 \item \textbf{How is the resolution of the instrument accounted for - are geometric instrument parameters scraped from the data file?} The resolution smearing of an instrument is described in detail at the top of page 6 when the \textbf{ReflectModel} is described.
-Constant dq/q or point by point dq/q resolution smearing can be used (Gaussian approximation), with the latter information being read from the 4th column of the dataset, this is also described in the manuscript.
+Constant $d\mathrm{q}/q$ or point by point $\mathrm{d}q/q$ resolution smearing can be used (Gaussian approximation), with the latter information being read from the 4th column of the dataset, this is also described in the manuscript.
 The manuscript also mentions that a resolution kernel of arbitrary shape can be used.
 However, it's not within the scope of the manuscript to describe the full mathematical detail of how those operations are performed.
-Besides the fourth column of the dataset (dq, if present) no other geometrical information is scraped from the datafile.
+Besides the fourth column of the dataset ($\mathrm{d}q$, if present) no other geometrical information is scraped from the datafile.
 This is because the inclusion of resolution information from various facilities is haphazard, and there is no standard dataset format.
@@
 
-\textbf{referee 2}
+\vskip12pt
+\noindent
+\textbf{Referee 2}
 \begin{itemize}
@@
 We are unsure why they are not rendered properly by the submission gateway.
-\item \textbf{In middle of page, Replace "user user" with "user"} This change is made.
+\item \textbf{In middle of page, Replace ``user user" with ``user"} This change is made.
 \item \textbf{Third-to-last line – shouldn't this read as $p(\theta|D,I)$ instead of $p(\theta|I,D)$?} The order of D, I does not really matter, but we have changed it anyway to be consistent with equation 1.
@@
 
-\textbf{referee 3}
+\vskip12pt
+\noindent
+\textbf{Referee 3} \\
 No amendments are required.
 
-\textbf{referee 4}
+\vskip12pt
+\noindent
+\textbf{Referee 4}
 \begin{itemize}
